\documentclass{article}

\usepackage{amsmath, amsthm, amssymb, amsfonts}
\usepackage{thmtools}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{float}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{framed}
\usepackage[dvipsnames]{xcolor}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{tikz-cd}

\colorlet{LightGray}{White!90!Periwinkle}
\colorlet{LightOrange}{Orange!15}
\colorlet{LightGreen}{Green!15}

\newcommand{\HRule}[1]{\rule{\linewidth}{#1}}
\newcommand{\Pf}[1]{$Proof.$\par}

\declaretheoremstyle[name=Definiton,]{thmsty}
\declaretheorem[style=thmsty,numberwithin=subsection]{definition}

\declaretheoremstyle[name=Theorem,]{thmsty}
\declaretheorem[style=thmsty,numberwithin=subsection]{theorem}


\declaretheoremstyle[name=Lemma,]{thmsty}
\declaretheorem[style=thmsty,numberlike=theorem]{lemma}

\declaretheoremstyle[name=Corollary,]{thmsty}
\declaretheorem[style=thmsty,numberlike=theorem]{corollary}

\declaretheoremstyle[name=Proposition,]{prosty}
\declaretheorem[style=prosty,numberlike=theorem]{proposition}

\declaretheoremstyle[name=Principle,]{prcpsty}
\declaretheorem[style=prcpsty,numberlike=theorem]{principle}

\declaretheoremstyle[name=Example,]{prcpsty}
\declaretheorem[style=prcpsty,numberwithin=subsection]{example}

\declaretheoremstyle[name=Ex,]{prcpsty}
\declaretheorem[style=prcpsty,numberwithin=section]{exercise}


\setstretch{1.2}
\geometry{
    textheight=9in,
    textwidth=5.5in,
    top=1in,
    headheight=12pt,
    headsep=25pt,
    footskip=30pt
}

% ------------------------------------------------------------------------------

\begin{document}

% ------------------------------------------------------------------------------
% Cover Page and ToC
% ------------------------------------------------------------------------------

\title{ \normalsize \textsc{}
		\\ [2.0cm]
		\HRule{1.5pt} \\
		\LARGE \textbf{\uppercase{Notes for Abstract Algebra}
		\HRule{2.0pt} \\ [0.6cm] \LARGE{Based on lectures provided by Dima Arinkin on MATH 742 2025 SPRING} \vspace*{10\baselineskip}}
		}
\date{}
\author{\textbf{Author} \\ 
		Wells Guan \\
		 \\
		}

\maketitle
\newpage

\tableofcontents
\newpage

% ------------------------------------------------------------------------------

\section{Rings and Ideals}

\subsection{Rings}

\begin{definition}(Ring)\par
    A ring $R$ is an abelian group with an associative multiplication distributive over the addition. (We always assume a ring has a multiplicative identity and commutative if not marked)\par
    A unit is an element $u$ with a reciprocal $1/u$ such that $u\cdot 1/u = 1$, which is also denoted $u^{-1}$ and called a numtiplicative inverse and the units form a multiplicative group, denoted $R^{\times}$.
\end{definition}

\begin{definition}
    (Homomorphism)\par
    A ring homomorphism is a ring map $\phi: R \to R'$ which preserving sums, products and $1$. If $R' = R$ we call $\phi$ an endomorphism and if it is also bijective we call it an automorphism.
\end{definition}

\begin{definition}
    (Subring)\par
    A subset $R'' \subset R$ is a buting if $R''$ is a ring and the inclusion $R'' \hookleftarrow R$ is a ring map. We call $R$ a extension of $R''$ and the inclusion an extension.\par
\end{definition}

\begin{definition}
    (Algebra)\par
    An $R$-algebra is a ring $R'$ that comes equipped with a ring homomorphism $\phi:R\to R'$ called the structure map. An $R$-algebta homormorphism $R'\to R''$ is a ring homomorphism between $R$-algebtas compatible with structure maps.\par
\end{definition}

\begin{definition}
    (Group action)\par
    A group $G $ is said to act on $R$ if there is a homomorphism given from $G$ into the group of automorphisms of $R$. The ring of invariants $R^G$ is the subring defined by
    \[R^G := \{x\in R|gx = g\text{ for all }g\in G\}\]
\end{definition}

\begin{definition}
    (Boolean)\par
    A ring $B$ is called Boolean if $f^2 = f$ for all $f\in B$, then $2f = 0$ since
    \[
    2f = (f+f)^2 = 4f
    \]
\end{definition}

\begin{definition}
    (Polynomial rings)\par
    Let $R$ be a ring, $P:=R[X_1,\cdots,X_n]$ the polynomial ring in $n$ variables. $P$ has the Universal Mapping Property (UMP), i.e. given a ring homomorphism $\phi:R\to R'$ and given an element $x_i$ of $R'$ for each $i$, there is a unique ring map $\pi:P\to R'$ with $\pi|_{R} = \phi$ and $\pi(X_i) = x_i$.\par
    Similarly, let $X:= \{X_{\lambda}\}_{\lambda \in \Lambda}$ be any set of variables. Set $P':=R[X]$ the elements of $P'$ are the polynomials in any finitely many of $X$.
\end{definition}

\begin{definition}
    (Ideals)\par
    Let $R$ be a ring. An ideal $I$ is a subset containing $0$ of $R$ such that $xa\in I$ for any $x\in R, a\in I$ and closed under addition.\par
    For a subset $S\subset R$, $\langle S\rangle$ means the smallest ideal containing $S$.\par
    Given a single element $a$, we say that the ideal $\langle a \rangle$ is principal. For a number of ideals $I_\lambda$, the sum $\sum I_{\lambda}$ mean the set of all finite linear combinations $\sum x_{\lambda}a_{\lambda}$ for $x_{\lambda} \in R, a_{\lambda}\in I_{\lambda}$. If $\Lambda$ is finite, then the product $\prod I_{\lambda}$ means the ideal generated by all products $\prod a_{\lambda}, a_{\lambda}\in I_{\lambda}$.\par
    For two ideals $I$ and $J$, the transporter of $J$ into $I$ mean the set
    \[(I:J):=\{x\in R|xJ\subset I\}\]
    If $I\subset J$ a subsring such that $I\neq J$, then we call $I$ proper.\par
    For a ring homomorphism $\phi:R\to R'$, $I\subset R$ a subring, denote by $IR'$ or $I^e$ the ideal of $R'$ generated by $\phi(I)$ can we call it the extension of $I$.\par
    Given an ideal $J$ of $R'$ and its preimage $\phi^{-1}(J)$ is an ideal of $R$ and we call ti the contraction of $J$ denoted with $J^c$.
\end{definition}

\begin{definition}
    (Residue Rings)\par
    Let $I$ be an ideal of $R$ and the cosets of $I$
    \[R/I := \{x+I|x\in R\}\]
    have a ring structure and it will be called the residue ring or quotient ring or factor ring of $R$ modulo $I$ and the quotient map:
    \[
    \kappa: R \to R/I,\quad \kappa(x) = x+I
    \]
    and $\kappa x$ is called the residue of $x$.
\end{definition}

\begin{proposition}\ \par
    For $I\subset R$ a subring and a ring homomorphism from $R$ to $R'$, then $\ker(\phi) \supset I$ implies that is a ring homomorphism $\psi:R/I \to R'$ with $\psi\kappa = \phi$.\par
    $\psi$ is surjective iff $\phi$ is surjective. $\psi$ is injective iff $I = \ker(\phi)$.
\end{proposition}

\begin{corollary}
    $R/\ker(\phi) \cong Im(\phi)$
\end{corollary}

\begin{proposition}\ \par
    $R/I$ is universal among $R$-algebras $R'$ such that $IR' = 0$, i.e. for $\phi:R\to R'$ such that $\phi(I) = 0$, there is a unique ring homomorphism $\psi:R/I \to R'$ such that $\psi \kappa = \phi$.
\end{proposition}

\begin{definition}
    The UMP serves to determine $R/I$ up to unique isomorphism, i.e. if $R'$ equipped with $\phi:R\to R'$ has the UMP too, then $R'$ is isomorphic to $R/I$.
\end{definition}
\Pf\par
    If $R'$ has the UMP among the $R$-algebras $R''$ such that $IR'' = 0$, then $\phi(I) = 0$ and hence there is a unique $\psi:R/I \to R'$ such that $\psi\kappa = \phi$ and since $\kappa I = 0$, we know there exists unique $\psi'$ such that $\psi'\phi = \kappa$ and then $(\psi'\psi)\kappa = \kappa$ and hence $\psi'\psi = 1$ and we are done by the uniqueness.

\begin{proposition}
    Let $R$ be a ring, $P:=R[X]$ the polynomial ring in one variable, $a\in R$ and $\pi:P\to R$ the $R$-algebra mao define by $\pi(X):=a$, then
    \begin{itemize}
        \item $\ker\pi = \{F(X)\in P|F(a) = 0\} = \langle X-a\rangle$
        \item $P/\langle X-a\rangle \cong R$
    \end{itemize}
\end{proposition}

\begin{definition}
    (Order of a polynomial)\par
    Let $R$ be a ring, $P$ the polynomial ring in variables $X_{\lambda}$ for $\lambda \in \Lambda$ and $(x_{\lambda}) \in R^{\Lambda}$ a vector. Let $\phi_{(x_{\lambda})}P\to P$ denote the $R$-algebra homomorphism defined by $\phi_{(x_{\lambda})}X_{\mu} := X_{\mu} + x_{\mu}$.\par
    The order of $F$ at the vector $(x_{\lambda})$ is defined as the smallest degree of monomials $M$ in $(\phi_{(x_{\lambda})}F)$.\par
    We know $\text{ord}_{(x_{\lambda})}F = 0$ iff $F(x_{\lambda}) \neq 0$.
\end{definition}

\begin{definition}
    Let $R$ be a ring, $I$ an ideal and $\kappa$ the quotient map. Given an ideal $J\supset I$ then the cosets
    \[
    J/I:=\{b+I|b\in J\} = \kappa(J)
    \]
    and then  $J/I$ is an ideal of $R/I$ and also $J/I = J(R/I)$.
\end{definition}

\begin{proposition}
    Given $J\supset I$ and we know
    \[
    \phi:R\to R/I\to (R/I)/(J/I)
    \]
    then we have the commutative diagram:
    \[
    \begin{tikzcd}
        R\arrow[r]\arrow[d] & R/J\arrow[d,"\cong"] \\
        R/I\arrow[r] & (R/I)/(J/I) \\
    \end{tikzcd}
    \]
\end{proposition}
\Pf\par
    Since $\phi(J) = 0$, so there exists unique $\psi:R/J \to (R/I)/(J/I)$ such that $\psi\kappa_J =\phi$ and since $\kappa_J(I) = 0$ and there exists $p$ such that $p\kappa_I = \kappa_J$ and consider $p(J/I) = 0$ and there exists $h$ such that $h\kappa_{(J/I)} = p$ and it is easy to check $h\psi = 1$ by uniqueness and we are done.

\begin{definition}\par
    Let $R$ be a ring. Let $e\in R$ be an idempotent, i.e. $e^2 = e$ then $Re$ is a ring with $e$ as multiplication unit, but $Re$ is not a subring unless $e=1$.\par
    Let $e':= 1-e$, then $e'$ is idempotent and $ee' = 0$ and we call them complementary idempotents.\par
    Denote $\text{Idem}(R)$ the set of all idempotents, which is close under a ring homomorphism.
\end{definition}

\begin{proposition}
    If $e_1,e_2\in R$ such that $e_1+e_2 = 1$ and $e_1e_2 =0$, then they are complementary idempotents.
\end{proposition}

\begin{definition}
    Let $R:R'\times R''$ be a product of two rings with componentwise operations.
\end{definition}

\begin{proposition}
    Let $R$ be a ring and $e',e''$ complementary idempotents. Set $R' := Re'$ and $R'' = Re''$. Define $\phi:R\to R'\times R''$ by $\phi(x) = (xe',xe'')$ and then $\phi$ is a ring isomorphism. $R' = R/Re''$ and $R'' = R/Re'$.
\end{proposition}
\Pf\par
    Check $\phi$ is surjective and injective.\par
    There is a natrual isomorphism between $I = \{(0,xe'')\} \subset R'\times R''$ and $R''$, and consider the diagram
    \[
    \begin{tikzcd}
        R\arrow[r] \arrow[d]& R'\times R''\arrow[l]\arrow[d] \\
        R/R'' & R'\times R''/I \\
    \end{tikzcd}
    \]
    and use the UMP.

\subsection{Prime Ideals}

\begin{definition}
    (Zerodivisors)\par
    Let $R$ be a ring. An element $x$ iscalled a zerodivisor if there is a nonzero $y$ such that $xy = 0$; otherwise, $x$ is called a nonzerodivisor. Denote the set of zerodivisors by $\text{z.div}(R)$ and the nonzerodivisors by $S_0$.
\end{definition}

\begin{definition}
    (Multiplicative subsets, prime ideals)\par
    Let $R$ be a ring. A subset $S$ is called multipliccative if $1\in S$ and $x,y\in S$ implies $xy\in S$.\par
    An ideal $P$ is called prime if its complement $R-p$ is multiplicative, or equivalentely, if $1\neq P$ and $xy\in P$ implies $x\in P$ or $y\in P$.
\end{definition}

\begin{definition}
    (Fields,domains)\par
    A ring is called a field if $1\neq 0$ and if every nonzero element is a unit.\par
    A ring is called an integral domain, or a domain if $\langle 0 \rangle$ or equivalently, if $R$ is nonzero and has no nonzero zerodivisors.\par
    Every domain $R$ is a subring of its fraction field $\text{Frac}(R):=\{x/y, x,y\in R\text{ and }y\neq 0\}$.
\end{definition}

\begin{proposition}
    Any subring $R$ of a field $K$ is a domain, and for a domain $R$, $\text{Frac}(R)$ has the UMP: the inclusion of $R$ into any field $L$ extends uniquely to an inclusion of $\text{Frac}(R)$ into $L$. 
\end{proposition}
\Pf\par
    For any subring $R$ of a field, $a,b\in R$, if $ab=0$, and $a$ nonzero, then $b = 0$ and we are done.\par
    If $\phi:R\hookrightarrow L$, then $\phi(x/y) = \phi(x)\phi(y)^{-1}$ is well-defined and obviously a ring homomorphism and we are done.

\begin{definition}
    (Polynomials over a domain)\par
    Let $R$ be a domain, $X$ a set of variable. $P:=R[X]$ and then $P$ is a domain, and $\text{Frac}(P)$ is called the rational functions.
\end{definition}

\begin{definition}
    (Unique factorization)\par
    Let $R$ be a domain, $p$ a nonzero nonunit. We call $p$ prime if $p|xy$ implies $p|x$ or $p|y$, which is equivalent with $\langle p\rangle$ is prime.\par
    For $x,y\in R$, we call $d\in R$ their gcd if $d|x$ and $d|y$ and if $c|x,c|y$ then $c|d$.\par
    $p$ is irreducible if $p=yz$ implies $y$ or $z$ is a unit. We call $R$ is a UFG if every nonzero nonunit factors into a product of irreducibles and the facrtotization is unique to order and units.
\end{definition}

\begin{proposition}
    If every nonzero nonunit factors have a factorization of a product of irreducible elements, then the factorization is unique up to order and units iff every irreducible element is prime.
\end{proposition}
\Pf\par
    
\begin{lemma}
    Let $\phi:R\to R'$ be a ring homomorphism, and $T\subset R'$ a subset. If $T$ is multiplicative, then $\phi^{-1}T$ is multiplicative; the converse holds if $\phi$ is surjective.
\end{lemma}
\Pf\par

\begin{proposition}
    Let $\phi:R\to R'$ be a ring map, and $J\subset R'$ an ideal. Set $I:=\phi^{-1}J$. If $J$ is prime, then $I$ is prime; the converse holds if $\phi$ is surjective.
\end{proposition}

\begin{corollary}
    Let $R$ be a ring, $I$ an ideal. Then $I$ is prime iff $R/I$ is a domain.
\end{corollary}
\Pf\par
    Consider
    \[
    \kappa:R\to R/I
    \]
    the quotient map and $I$ prime implies $\langle 0 \rangle$ is prime in $R/I$ and hence $R/I$ is a domain.

\begin{definition}
    (Maximal ideal)\par
    Let $R$ be a ring. An ideal $I$ is sai to be maximal if $I$ is proper and there is no proper ideal $J$ such that $I\subset J, I\neq J$.
\end{definition}

\begin{proposition}
    A ring $R$ is a field iff $\langle 0 \rangle$ is a maximal ideal.
\end{proposition}

\begin{corollary}
    Let $R$ be a ring, $I$ an ideal. Then $I$ is maximal iff $R/I$ is a field.
\end{corollary}
\Pf\par
    Only need to check $\langle 0 \rangle $ is maximal in $R/I$.

\begin{corollary}
    In a ring, every maximal ideal is prime.
\end{corollary}

\begin{definition}
    (Coprime)\par
    Let $R$ be a ring, and $x,y\in R$. We say $x$ and $y$ are coprime if their ideals $\langle x\rangle$ and $\langle y$ are comaximal.\par
    $x$ and $y$ are coprime if and only if there are $a,b\in R$ such that $ax+by = 1$.\par
\end{definition}

\begin{definition}
    A domain $R$ is called a Principal Ideal Domain if every ideal is principal. A PID is a UFD.
\end{definition}

\begin{theorem}
    Let $R$ be a PID. Let $P:=R[X]$ be the polynomial ring in one variable $X$, and $I$ a nonzero prime ideal of $P$. Then $P = \langle F\rangle$ with $F$ prime, or $P$ is maximal. Assume $P$ is maximal. Then either $P = \langle F\rangle $ with $F$ prime, or $P=\langle p, G\rangle$ with $p\in R$ prime, $pR = P\cap R$ and $G\in P$ prime with iamge $G'\in (R/pR)[X]$ prime.
\end{theorem}

\begin{theorem}
    Every proper ideal $I$ is contained in some maximal ideal.
\end{theorem}

\begin{corollary}
    Let $R$ be a ring, $x\in R$. Then $x$ is a unit iff $x$ belongs to non maximal ideal.
\end{corollary}

\subsection{Radicals}

\begin{definition}
    (Radical)\par
    Let $R$ be a ring. Its radical $\text{rad}(R)$ is defined to be the intersection of all its maximal ideals. 
\end{definition}

\begin{proposition}
    Let $R$ be a ring, $I$ an ideal, $x\in R$ and $u\in R^{\times}$. Then $x\in \text{rad}(R)$ iff $u-xy\in R^{\times}$ for all $y\in R$. In particular, the sum of an element of $\text{rad}(R)$ and a unit is a unit, and $I\subset \text{rad}(R)$ if $1-I\subset R^{\times}$.
\end{proposition}
\Pf\par
    For a maximal ideal $J$, if $u-xy\in J$, then $u\in J$ which is a contradiction and hence $u-xy$ is a unit. Conversely, if there exists $J$ maximal such that $x\in J$, then $\langle x\rangle + J = R$ and hence there exists $m\in J$ such that $u-xy = m$ for some unit $u$, which is a contradiction.\par

\begin{corollary}
    Let $R$ be a ring, $I$ an ideal, $\kappa:R\to R/I$ the quotient map. Assume $I\subset \text{rad}(R)$, then $\kappa$ is injective on $\text{Idem}(R)$.
\end{corollary}
\Pf\par
    For $e,e'\in \text{Idem}(R)$ and $x = e-e'$, if $\kappa(x) = 0$, then $x^3 = x$ and hence $x(1-x^2) = 0$, so $1-x^2$ is a unit and hence $x$ is $0$ and we are done.

\begin{definition}
    (Local ring)\par
    A ring is called local if it has exactly one maximal ideal, and semilocal if it has at least one and at most finitely many.\par
    By the residue field of a local ring $A$, we mean the field $A/M$ where $M$ is the maximal ideal of $A$.
\end{definition}

\begin{lemma}
    Let $A$ be a ring, $N$ the set of nonunits. Then $A$ is local iff $N$ is an ideal, if so, then $N$ is the maximal idal.
\end{lemma}
\Pf\par
    Only need to check the sufficiency, if $A$ is local, then we know $M$ is contained in $N$, and if there is $y\in M-N$, then $\langle y\rangle$ is a proper ideal and hence $y\in N$, which is a contradiction and hence $M=N$ and we are done.

\begin{proposition}
    Let $R$ be a ring, $S$ a multiplicative subset, and $I$ an ideal with $I\cap S = \emptyset$. Set $\mathcal{S} :=\{J,J\supset I, J\cap S = \emptyset\}$, then $\mathcal{S}$ has a maximal element $P$ and every such $P$ is prime.
\end{proposition}
\Pf\par
    By Zorn's lemma, their is a maximal element $P$ in $S$, for $x,y \in R - P$, there  exists $p,q\in P, a,b\in R$ such that $p+ax\in S, q+by \in S$ and hence $pq+pby+qax+abxy \in S$, and hence $xy\notin P$ and we are done.

\begin{definition}
    (Saturated multiplicative subsets)\par
    Let $R$ be a ring, and $S$ a multiplicative subset. We say $S$ is saturated if for $x,y\in R, xy\in S$, then $x,y\in S$.
\end{definition}

\begin{lemma}
    Let $R$ be a ring, $I$ a subset of $R$ that is stable under addition and multiplication, and $P_1,\cdots,P_n$ ideals such that $P_3,\cdots,P_n$ are prime. If $I$ is not contained in $P_j$ for all $j$, then there is an $x\in I$ such that $x\in P_j$ for $j$ or equivalently, if $I\subset \bigcup_{i=1}^n P_i$, then $I\subset I_i$ for some $i$.
\end{lemma}
\Pf\par
    If $n=1$ then we are done. We may use the induction, assume that $n\geq 2$, then by induction, for each $i$, there is $x_i\in I$ such that $x_i$ is not in $P_j, i\neq j$ and $x_i\in P_i$, so then $x_1+x_2\notin P_2$ if $n=2$. For other $n$, we will know $(x_1\cdots,x_{n-1})\notin P_j$ for all $j$.

\begin{definition}
    Let $R$ be a ring, $S$ a subset, its radical $\sqrt{S}$ is the set
    \[
    \sqrt{S}:=\{x\in R|x^n\in S\text{ for some }n\}
    \]
    If $I$ is an ideal and $I=\sqrt{I}$, then call $I$ to be radical.\par
    We call $\sqrt{0}$ is the nilradical and denoted as $\text{nil}(R)$. We call $x\in R$ nilpotent if $x\in \text{nil}(0)$, we call an ideal $I$ nilpotent if $a^n = 0$ for some $n\geq 1$.
\end{definition}

\begin{theorem}
    Let $R$ be a ring, $I$ an ideal, then
    \[
    \sqrt{I} = \cap_{P\supset I,P\text { prime}} P\]
\end{theorem}
\Pf\par
    For $x\notin\sqrt{I}$, let $S$ contains all the expotents of $x$ and $S$ is multiplicative, then $I\cap S = \emptyset$ and then there is an $P$ prime containing $I$ with not containing $x$ and hence $\sqrt{a}$ contains the union.\par
    Converse direction is easy.

\begin{proposition}
    Let $R$ be a ring, $I$ an ideal. Then $\sqrt{I}$ is an ideal.
\end{proposition}

\begin{definition}
    (Minimal primes)\par
    Let $R$ be a ring, $I$ an ideal and $P$ prime. We call $P$ a minimal prime of $I$ if $P$ is minimal in the set of primes containing $I$, we all $P$ a minimal prime of $R$ if $P$ is a minimal prime of $\langle 0 \rangle$.
\end{definition}

\begin{proposition}
A ring $R$ is reduced, i.e. $0$ is the only nilpotent, and has only one minial prime iff $R$ is a domain.
\end{proposition}
\Pf\par
    Converse direction is obvious. If $0$ is the only nilpotent elements, $Q$ is a minimal prime ideal, then $Q = 0$ since $0$ is the intersection of all the minimal primes, and we are done. 

\subsection{Modules}

\begin{definition}
    (Modules)\par
    Let $R$ be a ring. An $R$-module $M$ is an abelian group with a scalar multiplication
    $R\times M \to M$ which is
    \begin{itemize}
        \item $x(m+n) = xm+xn$ and $(x+y)m = xm + ym$
        \item $x(ym) = (xy)m$
        \item $1m = m$
    \end{itemize}\par
    A submodule $N$ of $M$ closed under scalar multiplication.\par
    Given $m\in M$, its annihilator
    \[
    \text{Ann}(m):=\{x\in R|xm = 0\}
    \]
    and the annilhilator of $M$ is
    \[
    \text{Ann}(M):=\{x\in R|xm = 0\text{ for all }m\in M\}
    \]
    We call the intersection of all maximal ideals containing $Ann(M)$ the radical of $M$, denoted as $\text{rad}(M)$.\par   
\end{definition}

\begin{proposition}
    There is a bijection between the maximal ideals containing $\text{Ann}(M)$ and the maximal ideals of $R/\text{Ann}(M)$, and hence
    \[
    \text{rad}(R/\text{Ann}(M)) = \text{rad}(M) /\text{Ann}(M)
    \]
\end{proposition}

\begin{proposition}
    Given a submodule $N$ of $M$, and then $\text{Ann}(M) \subset \text{Ann}(N)$ and we also have $\text{Ann}(M) \subset \text{Ann}(M/N)$.
\end{proposition}

\begin{definition}
    (Semilocal)\par
    We call $M$ semilocal if there are only finitely many maximal ideals containing $\text{Ann}(M)$. If $R$ is semilocal, so is $M$ and we will know $M$ is semilocal iff $R/\text{Ann}(M)$ is a semilocal ring.
\end{definition}

\begin{definition}
    (Polynomials)\par
    The sets of polynomials
    \[
    M[X] :=\{\sum\limits_{i=0}^n m_iM_i, M_i\text{ monomials}\}
    \]
    and then $M[X]$ is an $R[X]-module$.
\end{definition}

\begin{definition}
    (Homomorphisms)\par
    Let $R$ be aring, $M$ and $N$ modules. A $R$-linear map is a map $\alpha:M\to N$ such that
    \[
    \alpha(xm+yn) = x\alpha m + y\alpha n
    \]
    Let $\iota:\ker\alpha \to M$ be the inclusion and then $\ker\alpha$ has the UMP: $\alpha\iota = 0$ and for a homomorphism $\beta:K\to M$ with $\alpha\beta = 0$, there is a unique homomorphism $\gamma:K\to \ker\alpha$ with $\iota\gamma = \gamma$ as shown below
    \[
    \begin{tikzcd}
        \ker\alpha\arrow[r,"\iota"] & M\arrow[r,"\alpha"] & N \\
        &K\arrow[lu,"\gamma"]\arrow[u,"\beta"]\arrow[ru,"0"]& \\
    \end{tikzcd}
    \]
\end{definition}

\begin{definition}
    (Endomorphism)\par
    An endomorphism of $M$ a self-homomorphism denoted as $\text{End}_R(M) \subset \text{End}_{\mathbb{Z}}(M)$.\par
    For $x\in R$, let $\mu_x$ the self map of multiplication by $x$ and then $x\mapsto \mu_x$ denoted as
    \[\mu_R:R\to \text{End}_R(M)\]
    and note that $\ker\mu_R = \text{Ann}(M)$.
    We call $M$ faithful if $\mu_R$ is injective.
\end{definition}

\begin{definition}
    For two rings $R$ and $R'$, suppose $R'$ is an $R$-algebra and $M'$ an $R'$-module, then $M'$ is also an $R$-module by $xm:= \phi(x)m$.\par
    A subalgebra $R''$ of $R'$ is a subring such that the structure map owning image in $R''$. The subalgebra generated by $x_{\lambda} \in R'$ for $\lambda \in \Lambda$ is the smallest $R$-subalgebra containing $x_{\lambda}$ and we denote it by $R[\{x_{\lambda}\}]$ and we call $x_{\lambda}$ the generators.\par
    We say $R'$ is a finitely generated $R$-algebra if there exists $x_i, 1\leq i \leq n$ such that $R' = R[x_1,\cdots,x_n]$.
\end{definition}

\begin{definition}
    (Residue modules)\par
    Let $R$ be a ring, $M $a module and $M'\subset M$ a submodule. Then
    \[
    M/M':=\{m+M'|m\in M\}
    \]
    which is the residue module or M modulo M', form the quotien map
    \[\kappa:M\to M/M',\quad m\mapsto m+M'\]
\end{definition}

\begin{definition}
    (Cyclic Modules)\par
    Let $R$ be a ring. A module $M$ is said to be cyclic if there exists $m\in M$ such that $m = Rm$, then $\alpha:x\mapsto xm$ induces an isomorphism $R/\text{Ann}(m) \cong M$.
\end{definition}

\begin{definition}
    (Noether Isomorphisms)\par
    Let $R$ be a ring, $N$ a module, and $L$ and $M$ submodules.\par
    Assume $L\subset M$, and
    \[
    \alpha:N\to N/L \to (N/L)/(M/L)
    \]
    and we may know $\ker \alpha = M$. then $\alpha$ factors through the isomorphism $\beta$ in $N\to N/M \to (N/L)/(M/L)$ since $\alpha$ is surjective and $\ker\alpha = M$, so
    \[
    \begin{tikzcd}
        N\arrow[r]\arrow[d] & N/M\arrow[d,"\beta"] \\
        N/L\arrow[r] & (N/L)/(M/L) 
    \end{tikzcd}
    \]
    Assume $L$ not in $M$ and
    \[
    L+M:=\{l+m, l\in  L, m\in M\}
    \]
    and it will be a submodule, then similarly
    \[
    \begin{tikzcd}
        L\arrow[r]\arrow[d] & L/(L\cap M)\arrow[d,"\beta"] \\
        L+M\arrow[r] & (L+M)/M 
    \end{tikzcd}
    \]
 \end{definition}

\begin{definition}
    (Cokernels, coimages)\par
    Let $R$ be a ring, $\alpha:M\to N$ linear. Associated to $\alpha$ there are its cokernel and its coimage
    \[
    \text{Coker}(\alpha) := N/\text{Im}(\alpha)\quad \text{Coim}(\alpha):= M/\ker{\alpha}
    \]
\end{definition}

\begin{definition}
    (Generators, free modules)\par
    Let $R$ be a ring, $M$ a module. Given some submodules $N_{\lambda}$, by the sum $\sum N_{\lambda}$, we mean the set of all finite linear combinations $\sum x_{\lambda}m_{\lambda}, m_{\lambda} \in N_{\lambda}$.\par
    Elements $m_{\lambda}$ are said to be free of linearly independent if the linear combination equals to zero implies zero coefficients. If $m_{\lambda}$ are said to be form a (free) basis of $M$, then they are free and generate $M$ and we say $M$ is free on $m_{\lambda}$.\par
    We say $M$ is finitely generated if it has a finite set of generators and $M$ is free if it has a free basis.
\end{definition}

\begin{theorem}
    Let $R$ be a PID, $E$ a free module with $e_{\lambda}$ a basis, and $F$ a submodule, then $F$ is free and has a basis indexed by a subset of $\lambda$.
\end{theorem}

\begin{definition}
    Let $R$ be a ring, $\Lambda$ a set, $M_{\lambda}$ a module for $\lambda\in\Lambda$. The direct product of $M_{\lambda}$ is the set of any vectors
    \[
    \prod M_{\lambda} := \{(m_{m_{\lambda}})\}
    \] 
    which is a module under componentwise addition and scalar multiplication.\par
    The direct sum of $M_{\lambda}$ is the subset of restricted vectors:
    \[
    \bigoplus M_{\lambda} := \{({m_{\lambda}}), m_{\lambda}\text{ nonzero for only finite elements}\}
    \]
\end{definition}

\begin{proposition}
    $\prod M_{\lambda}$ has the UMP,  for $R$-homomorphism $\alpha_{\kappa}:L\to M_{\kappa}$, there is a unique $R$-homomorphism $L\to \prod M_{\lambda}$ such that $\pi_{\kappa}\alpha = \alpha_{\kappa}$, in other words, $\pi_{\lambda}$ induce a bijection of
    \[\text{Hom}(L,\prod M_{\lambda}) \cong \prod \text{Hom}(L,M_{\lambda})\]
    Similarly, the direct sum comes equipped with injections
    \[\iota_{\kappa} \to \bigoplus M_{\lambda}\]
    and it has the UMP: given $\beta_{\kappa}:M_{\kappa} \to N$, there is a unique $R$-homomorphism $\beta:\bigoplus M_{\lambda} \to N$ such that $\beta \iota_{\kappa} = \beta_{\kappa}$ and $\iota_{\kappa}$ induce the bijection:
    \[\text{Hom}(\bigoplus, N) \to \bigoplus \text{Hom}(M_{\lambda, N})\]
\end{proposition}

\subsection{Exact Sequences}

\begin{definition}
    (Exact)\par
    A sequence of module homomorphisms
    \[
    \cdots \to M_{k-1}\overset{\alpha_{k-1}}{\to} M_k \overset{\alpha_k}{\to} M_{k+1} \to \cdots
    \]
    is said to be exact at $M_k$ if $\ker\alpha_k = \text{Im}(\alpha_k)$. The sequence is said to be exact if it is exact at every $M_k$, except an initial source of final target.
\end{definition}

\begin{definition}
    (Short exact sequences)\par
    A sequence $0\to L \overset{\alpha}{\to} M \overset{\beta}{\to} N \to 0$ is exact if and only if $\alpha$ is injective and $N \cong \text{Coker}\alpha$ or dually if and only if $\beta$ is surjective and $L =\ker\beta$. Then the sequence is called short exact and we often regard $L$ as a submodule of $M$ and $N$ the quotient $M/L$.
\end{definition}
\Pf\par

\begin{proposition}
    For $\lambda \in \Lambda$, let $M_{\lambda}' \to M_{\lambda} \to M_{\lambda}''$ be sequence of module homomorphisms. If every sequence is exact, then so are the two induced sequences
    \[
    \bigoplus M_{\lambda}' \to \bigoplus M_{\lambda} \to \bigoplus M_{\lambda}'', \quad \prod M_{\lambda}' \to \prod M_{\lambda} \to \prod M_{\lambda}'' 
    \]
    Conversely, if either induced sequence is exact then so is every original one.
\end{proposition}
\Pf\par

\begin{proposition}
    Let $0\to M'\overset{\alpha}{\to} M \overset{\beta}{\to} M'' \to 0$ be a short exact sequence, and $N\subset M$ a submodule. Set $N':=\alpha^{-1}(N)$ and $N'':= \beta(N)$. Then the induced sequence $0 \to N' \to N \to N'' \to 0$ is short exact.
\end{proposition}

\begin{definition}
    (Retraction, section, splits)\par
    A linear map $\rho: M \to M'$ is a retraction of another $\alpha:M'\to M$ if $\rho\alpha = 1_{M'}$, then $\alpha$ is injective and $\rho$ is surjective.\par
    Dually, we call $\sigma:M''\to M$ a section of another $\beta:M\to M''$ if $\beta\sigma = 1_{M''}$, then $\beta$ is surjective and $\sigma$ is injective.\par
    We call a $3$-term exact sequence $M' \overset{\alpha}{\to} M \overset{\beta}{\to} M''$ splits if there is an isomorphism $\phi:M\cong M'\oplus M''$ with $\phi\alpha = \iota_{M'}$ and $\beta = \pi_{M''}\phi$.
\end{definition}
    
\begin{proposition}
    Let $M'\overset{\alpha}{\to}M\overset{\beta}{\to}M''$ be a $3$-term exact sequence. Then the following conditions are equivalent
    \begin{itemize}
        \item The sequence splits
        \item There exists a retraction $\rho:M\to M'$ of $\alpha$ and $\beta$ is surjective.
        \item There exists a section $\sigma:M'' \to M$ of $\beta$ and $\alpha$ is injective
    \end{itemize}
\end{proposition}
\Pf\par
    Assume the sequence is splits, then we have the commuting diagram
    \[
    \begin{tikzcd}
        M'\arrow[r,"\alpha"]\arrow[rd,"\iota_{M'}"] & M\arrow[r,"\beta"]\arrow[d,"\phi(\cong)"] & M'' \\
        & M'\oplus M''\arrow[ru,"\pi_{M''}"] & \\
    \end{tikzcd}
    \]
    then let $\rho = \pi_{M'}\phi$, then $\rho\alpha = \pi_{M'}\phi \phi^{-1}\iota_{M'} = 1_{M'}$. Let $\sigma = \phi^{-1}\iota_{M''}$ and then $\beta\sigma = \pi_{M''}\phi\phi^{-1}\iota_{M''} = 1_{M''}$ and then $\beta$ is surjective and $\alpha$ is injective.\par
    Now assume there is such a retraction $\rho$ and $\beta$ is surjective, then define $\sigma = 1_M - \alpha\rho$ and $\phi: M \to M'\oplus M''$ by $m\mapsto (\rho(m),\beta\sigma(m))$., if $\phi(m) = 0$, then $\rho(m) = 0$ and $\sigma(m) = m$, which means $\beta(m) = 0$. There exists $a\in M'$ such that $m = \alpha(a)$ and hence $a = 0$ which means $m = 0$, so $\ker\phi = 0$. For $(a,b)\in M'\oplus M''$, assume $\beta(m) = b$, then $\phi(\alpha(a) + \sigma(m)) = (a+\rho(m-\alpha\rho(m)), \beta(\alpha(a)) + \beta(\sigma(m))) = (a,b)$ and hence $\phi$ is surjective. And $\phi\alpha(a) = (a,\beta\sigma\alpha(a)) = (a,0)$ and $\pi_{M''}\phi(m) = \beta(\sigma(m)) = \beta(m)$ and we are done.\par

\begin{lemma}
    Consider this commutative diagram with exact rows:
    \[
    \begin{tikzcd}
        & M'\arrow[r,"\alpha"]\arrow[d,"\gamma'"] & M\arrow[r,"\beta"]\arrow[d,"\gamma"] & M''\arrow[r]\arrow[d,"\gamma''"] & 0\\
        0\arrow[r]& N'\arrow[r,"\alpha'"] & N\arrow[r,"\beta'"] & N'' & \\
    \end{tikzcd}
    \]
    It yields the following exact sequence:
    \[\ker\gamma' \overset{\varphi}{\to} \ker\gamma \overset{\psi}{\to} \ker\gamma'' \overset{\partial}{\to} \text{coker}\gamma' \overset{\varphi'}{\to} \text{coker}\gamma \overset{\psi'}{\to} \text{coker}\gamma''\]
    Moreover, if $\alpha$ is injective, then so is $\varphi$; dually, if $\beta'$ is surjective, then so is $\psi'$.
\end{lemma}
\Pf\par
    Notice $\alpha'\gamma' = \gamma\alpha, \beta'\gamma = \gamma''\beta$ and let $\varphi = \alpha|_{\ker\gamma'},\psi = \beta|_{\ker\gamma}$ and we know $\varphi(\ker\gamma') \subset\ker\gamma, \psi(\ker\gamma) \subset \ker\gamma''$. Obviously, $\text{Im}(\varphi) \subset \ker\psi$ and for any $b\in \ker\psi$, it is in $\ker\gamma \cap \text{Im}\alpha$, since $\alpha'$ is injective and hence its preimage has to be contained in $\ker\gamma'$ and hence it is in $\text{Im}(\varphi)$.\par
    $\alpha',\beta'$ will induce natural $\varphi',\psi'$ on $\text{coker}\gamma',\text{coker}\gamma$ by defining $n'+\text{Im}\gamma'\mapsto \alpha'(n')+\text{Im}\gamma, n+\text{Im}\gamma \mapsto \beta'(n)+\text{Im}\gamma''$, which is well-defined since $\alpha'(\text{Im}\gamma') \subset \text{Im}\gamma, \beta'(\text{Im}\gamma)\subset \text{Im}\gamma''$ and the exactness is similarly checked.\par
    Define $\partial$ by the following, if $\gamma'' m'' = 0$, consider $m$ is one of preimage of $m''$ and let $a$ to be the preimage of $\gamma(m)$, then let $\partial m'' = a+\text{Im}\gamma'$. It is well-defined since if $\beta m = \beta n = m''$, then $m-n\in \ker\beta $, which means the preiamges of $\gamma m, \gamma n$ are in the same coset. For $m\in \ker \gamma$, $\partial(\psi(m)) = \alpha'^{-1}\gamma(m) + \text{Im}\gamma' = 0$ and if $\partial(m'') = 0$, then assume $\beta m =m''$ and we know $\alpha^{-1}\gamma(m) \in \text{Im}\gamma'$ and hence there exists $x\in M'$ such that $\gamma\alpha x = \gamma m$ and we know $ \beta(m-\alpha(x)) = m''$ and $\gamma(m-\alpha x) = 0$, which means $\ker \partial = \text{Im}\psi$. If $a = \alpha'^{-1}(\gamma(m))$ with $m'' = \beta m \in \ker \gamma''$, then $\varphi'(a+\text{Im}(\gamma')) = \alpha' a + \text{Im} \gamma = 0$ and if $\varphi'(a+\text{Im}(\gamma')) = 0$, then there exists $m$ such that $\alpha'(a) = \gamma m$ and then $\partial(\beta(m)) = a+\text{Im}\gamma'$ and we are done.

    \begin{theorem}
        (Left exactness of Hom)\par
        \begin{itemize}
            \item Let $M' \to M \to M'' \to 0$ be a sequence of linear maps. Then it is exact iff for all modules $N$, the following induced sequence is exact
            \[0 \to \hom(M'',N) \to \hom(M,N) \to \hom(M',N)\]
            \item Let $0\to N' \to N \to N''$ be as sequence of linear maps. Then it is exact iff for all modules $M$, the following induced sequence is exact.
            \[0 \to \hom(M,N') \to \hom(M,N) \to \hom(M,N'')\]
        \end{itemize}
    \end{theorem}
    \Pf\par
        Assume $M'\overset{\phi}{\to} M \overset{\psi}{\to} M''$ and then the induced map will be $\tilde{\psi}: f\mapsto f\circ \psi$ and $\tilde{\phi}:g\mapsto g\circ \phi$. If $\psi$ is surjective, then $\tilde{\psi}$ will be an injective since $f\circ\psi = 0$ implies $f = 0$, and if $g\circ\phi = 0$, then $ \ker \psi = \text{Im} \phi \subset \ker{g}$ and hence there will be $g':M'' \cong M/\ker\psi \to N$ such that $g'\psi = g$ by the UMP and we are done. We know for $g:M \to N, g\circ \phi = 0$, equivalently  $\text{Im}\phi \subset \ker g$ iff there exists unique $g':M''\to N$ such that $g' \circ \psi = g$, which means $M''\cong \text{coker}\phi$ and the diagram
        \[
        \begin{tikzcd}
            M'\arrow[r,"\phi"] & M\arrow[r,"\psi"]\arrow[rd,"\kappa"] & M''\arrow[d]\arrow[r] & 0 \\
            & & \text{coker}\phi\arrow[u]\arrow[ru] & \\
        \end{tikzcd}
        \]
        commutes and we are done.\par
        Similarly assume that $N'\overset{\phi}{\to} N \overset{\psi}{\to} N''$, then $\tilde{\phi}: f\mapsto \phi\circ f$ and $\tilde{\psi}: g\mapsto \psi\circ g$, which means $\ker\psi = N'\hookrightarrow N$. It is easy to check $\ker\tilde{\phi} = 0$ and $\text{Im}\tilde{\phi} \subset \ker\tilde{\psi}$. For $g\in\ker \tilde{\psi}$, since $\text{Im}g \subset \ker\psi = \text{Im}\phi$, then let $g' = g|_N$ will satisfy that $\phi\circ g' = g$. For the converse direction, we know for any $g:M\to N$, $\text{Im}g\subset \ker\psi$ iff there exists a unique $g':M\to N'$ such that $\phi \circ g' = g$, then we may, which is 
        \[
        \begin{tikzcd}
            0\arrow[r]\arrow[rd] & N'\arrow[r,"\phi"] & N\arrow[r,"\psi"] & N'' \\
              & \ker\psi\arrow[hookrightarrow]{ru} & & \\
        \end{tikzcd}
        \]

    \begin{definition}
        (Presentation)\par
        A (free) presentation of a module $M$ is an exact sequence
        \[G\to F \to M \to 0\]
        with $G$ and $F$ free. If $G$ and $F$ are free of finite rank, then the presentation is called finite. If $M$ has a finite presentation, then call $M$ finitely presented.
    \end{definition}

    \begin{proposition}
        Let $R$ be a ring, $M$ a module, $m_{\lambda}$ generators. Then there is an  exact sequence $0\to K \to R^{\oplus\Lambda} \overset{\alpha}{\to} M \to 0$ with $\alpha e_{\lambda} = m_{\lambda}$ where $e_{\lambda}$ the standard basis and there is a presentation.
    \end{proposition}
    $Remark.$\par
    Choose $K = \ker \alpha$ and $k_{\sigma}, \sigma\in\Sigma$ to be generators of $K$, then 
    \[R^{\oplus \Sigma} \to R^{\oplus\Lambda} \to M \to 0\]
    is a presentation.

    \begin{definition}
        (Projective Module)\par
        A module $P$ is called projective if given any surjective linear map $\beta:M\to N$, every linear map $\alpha:P\to N$ lifts to one $\gamma:P\to M$, i.e. $\alpha = \beta\gamma$.
    \end{definition}

    \begin{theorem}
        The following conditions on an $R$-module $P$ are equivalent
        \begin{itemize}
            \item The module $P$ is projective
            \item Every short exact sequence $0\to K \to M \to P \to 0$ splits
            \item There is a module $K$ such that $K\oplus P$ is free
            \item Every exact sequence $N'\to N \to N''$ induces an exact sequence
            \[\hom(P,N) \to \hom(P,N) \to \hom(P,N'')\]
            \item Every surjective homomophism $\beta:M \to N$ induces a surjection
            \[\hom(P,\beta):\hom(P,M)\to \hom(P,N)\]
        \end{itemize}
    \end{theorem}
    \Pf\par
    By considering the $P\cong M/\ker \phi$ it will induce a section of $\psi:M\to P$ and obviously $\phi:K\to M$ is injective and we are done for (1) implies (2). Use proposition 1.5.6. and we will know there exists $K$ such that $K\oplus P \cong R^{\oplus \Lambda}$ which is free, which is for (2) implies (3). Assume (3), then there exists $\Lambda$ such that $K\oplus P \cong R^{\oplus \Lambda}$. Also notice that we will have
    \[\prod N_{\lambda}' \to \prod N_{\lambda} \to \prod N_{\lambda}''\]
    is exact, which implies that
    \[\hom(R^{\oplus \Lambda}, N') \to \hom(R^{\oplus \Lambda}, N) \to \hom(R^{\oplus \Lambda}, N'')\]
    is exact since $\hom(R^{\oplus \Lambda},N) \cong \prod N_{\lambda}$ and hence
    \[
    \hom(K\oplus P, N') \to \hom(K\oplus P, N) \to \hom(K\oplus P, N'')
    \]
    which implies
    \[
    \hom(K,N')\oplus\hom(P,N') \to \hom(K,N)\oplus\hom(P,N) \to \hom(K,N'')\oplus\hom(P,N'')
    \]
    by isomorphism and hence the conclusion goes.\par
    Assume (4), we know $M \to N \to 0$ is exact and we are done.\par
    Assume (5), which is exactly the definition of projective module.

    \begin{lemma}
        (Schanuel)\par
        Any two short exact sequences
        \[0\to L \overset{i}{\to} P \overset{\alpha}{\to} M \to 0,\quad 0 \to L' \overset{i'}{\to} P' \overset{\alpha'}{\to} M \to 0\]
        with $P$ and $P'$ projective are essentially isomorphic; i.e. there is the following commutative diagram
        \[
        \begin{tikzcd}
            0\arrow[r] & L\oplus P'\arrow[r,"i\oplus 1_{P'}"]\arrow[d,"\cong\ \beta"] & P\oplus P'\arrow[r,"\alpha\oplus 0"]\arrow[d,"\cong\ \gamma"] & M\arrow[d,"="]\arrow[r] & 0 \\
            0\arrow[r] & P\oplus L'\arrow[r,"1_P\oplus i'"] & P\oplus P'\arrow[r,"0\oplus\alpha'"] & M\arrow[r] & 0
        \end{tikzcd}
        \]
    \end{lemma} 
    \Pf\par
        Firstly, it is easy to check the two exact sequences are exact. Then consider
        \[
        0 \to K:=\ker(\alpha\oplus\alpha') \to P\oplus P' \to M \to 0
        \]
        which is exact, there exists $\pi:P'\to P$ such that $\alpha\pi = \alpha'$, so we may define $\phi:P\oplus P' \to P\oplus P'$ by $\left(\begin{array}{cc}
        1_P & \pi \\
        0 & 1_P' 
        \end{array}\right)$ which means $(p,p')\mapsto (p+\pi p',p')$ and then $\alpha p+\alpha' p' = (\alpha\oplus 0)\phi(p,p') = (\alpha\oplus\alpha')(p,p')$ where the inverse of $\phi$ will be $\left(\begin{array}{cc}
        1_P & -\pi \\
        0 & 1_P' 
        \end{array}\right)$ and hence $\phi$ is an automorphism.\par
        Notice $L$ is $\ker \alpha$, and for $(p,p') \in L\oplus P'$, denoted $\psi:L\oplus P' \to K$ the induced map by $\phi^{-1}$ and then $\psi(p,p') = (p-\pi p' ,p')$ which is in $\ker(\alpha\oplus \alpha')$ and it has inverse obviously, and hence $L\oplus P' \cong K$, and use the similar construction to $P\oplus L'$ and we are done.
    \begin{proposition}
        Let $R$ be a ring, and $0\to M \to N \to M' \to 0$ an exact sequence. Prove $M,M'$ are finitely generated implies $N$ is finitely generated.    
    \end{proposition}
    
    \begin{proposition}
        Let $R$ be a ring, and $0\to L \to R^n\to M \to 0$ an exact sequence. Prove $M$ is finitely generated iff $L$ is finitely presented.    
    \end{proposition}
    
    \begin{proposition}
        Let $0\to L \overset{\alpha}{\to} M \overset{\beta}{\to} N \to 0$ be a short exact sequence with $L$ finitely generated and $M$ finitely presented. Then $N$ is finitely presented.
    \end{proposition}
    \Pf\par
        There exists $G\to F \to M \to 0$ exact with $G,F$ free of finite rank. Let $\mu:R^m \to M$ any surjection and $\nu:= \beta\mu$, let$K = \ker \nu$ and $\lambda = \mu|_K$, then the diagram
        \[
        \begin{tikzcd}
            0\arrow[r] & K\arrow[r]\arrow[d,"\lambda"] & R^m\arrow[r,"\nu"]\arrow[d,"\mu"] & N\arrow[r]\arrow[d,"1_N"] & 0 \\
            0\arrow[r] & L\arrow[r,"\alpha"] & M\arrow[r,"\beta"] & N\arrow[r] & 0 \\
        \end{tikzcd}
        \]
        commutes and the snake lemma ensure that $\ker\lambda \cong \ker\mu$, however $\ker\mu$ is finitely generated and hence $\ker\lambda$ is finitely generated, and snake lemma ensured that $\text{coker}\lambda = 0$ and hence $0\to \ker\lambda \to K \to L \to 0$ is exact and hence $K$ is finitely generated and hence $N$ is finitely presented.

    \begin{proposition}
        Let $0\to L \overset{\alpha}{\to} M \overset{\beta}{\to} N \to 0$ be a short exact sequence with $L,N$ finitely presented. Then $M$ is finitely presented.
    \end{proposition}
    \Pf\par
        Let $\lambda:R^l \to L, \nu:R^n \to N$ any two surjections and define $\gamma: = \alpha\lambda$ and since $R^n$ is projective, then define $\delta:R^n \to M$ by lifting $\nu$ and $\mu:R^l\oplus R^n \to M$ by $\gamma+\delta$ and the diagram
        \[
        \begin{tikzcd}
            0\arrow[r] & R^l\arrow[r]\arrow[d,"\lambda"] & R^l\oplus R^n\arrow[r,"\nu"]\arrow[d,"\mu"] & R^n\arrow[r]\arrow[d,"\nu"] & 0 \\
            0\arrow[r] & L\arrow[r,"\alpha"] & M\arrow[r,"\beta"] & N\arrow[r] & 0 \\
        \end{tikzcd}
        \]
        commutes, and the snake lemma yields that
        \[0\to \ker \lambda \to \ker\mu \to \ker\nu \to 0\]
        exact and $\text{coker}\mu = 0$ and $\ker\lambda,\ker\mu$ are finitely generated and hence $\ker \mu$ is ginitely generated and hence $M$ is finitely presented.

\subsection{Direct Limits}

\begin{definition}
    (Categories)\par
    A category $\mathcal{C}$ is a collection of elements, called objects. Each pair of objects $A,B$ is equipped with a set $\hom_{\mathcal{C}}(A,B)$ called maps or morphisms. For objects $A,B,C$, there is a composition law
    \[\hom_{\mathcal{C}}(A,B) \times \hom_{\mathcal{C}}(B,C) \to \hom_{\mathcal{C}}(A,C),\quad (a,\beta) \to \beta\alpha\]
    and there is a distinguished map $1_B \in \hom_{\mathcal{C}}(B,B)$ such that
    \[
    \gamma(\beta\alpha) = (\gamma\beta)\alpha\text{ for any }\gamma:C\to D,\quad\text{ and }1_B\alpha= \alpha, \beta 1_B = \beta
    \]
    and we say $\alpha$ is an isomorphism with inverse $\beta:B\to A$ such that $\alpha\beta = 1_B$ and $\beta\alpha = 1_A$.
\end{definition}

\begin{definition}
    (Functors)\par A map of categories is known as a functor. Namely, given categories $\mathcal{C}$ and $\mathcal{C}'$, a functor $F:C\to \mathcal{C}'$ is a rule that assigns to each object $A$ of $\mathcal{C}$ and $F(A)$ of $\mathcal{C}'$ and to each map $\alpha$ such that $F(\alpha):F(A)\to F(B)$
    \[
    F(\beta\alpha) = F(\beta)F(\alpha),\quad F(1_A) = 1_{F(A)}
    \]\par
    A map of functors is known as a matural transformation. Given two functors $F,F':\mathcal{C} \to \mathcal{C}'$, a natrual transformation $\theta:F\to F'$ is a collection of maps $\theta(A):F(A) \to F'(A)$ such that $\theta(B)F(\alpha) = F'(\alpha)\theta(A)$ for any $\alpha$ and $1_{F(A)}$ trvially form a natrual transformation $1_F$. We call $F$ and $F'$ isomorphic if there are natural transformation $\theta:F\to F'$ and $\theta' : F'\to F$ such that $\theta'\theta = 1_F$ and $\theta\theta' = 1_{F'}$.\par
    A contravariant functor $G$ from $C$ to $C'$ is a rule similar to $F$ but $G(\alpha):G(B)\to G(A)$ with analogous properties with functors.
\end{definition}

\begin{definition}
    (Adjoint)\par
    Let $F:\mathcal{C} \to  \mathcal{C}'$ and $F':\mathcal{C}' \to  \mathcal{C}$ be functors. We call $(F,F')$ an adjoint pair , $F$ the left adjoint of $F'$ and $F'$ the right-adjoint of $F$ if for any $A\in\mathcal{C}$ and $A'\in\mathcal{C'}$, there is given a natural bijection
    \[\hom_{\mathcal{C'}}(F(A),A') \cong \hom_{\mathcal{C}}(A,F'(A'))\]
    here natural means that maps $B\to A$ and $A'\to B'$ induce a commutative diagram:
    \[
    \begin{tikzcd}
        \hom_{\mathcal{C'}}(F(A),A')\arrow[d]\arrow[r,"\cong"]& \hom_{\mathcal{C}}(A,F'(A'))\arrow[d] \\
        \hom_{\mathcal{C'}}(F(B),B')\arrow[r,"\cong"] & \hom_{\mathcal{C}}(B,F'(B'))
    \end{tikzcd}
    \]
\end{definition}

\begin{proposition}
    Naturality serves to determine an adjoint up to canonical isomorphism. Namely, let $F$ and $G$ be two left adjoints of $F'$ and then $F$ and $G$ are isomorphic.
\end{proposition}
\Pf\par
    Define $\theta(A):G(A) \to F(A)$ by the image of $1_{F(A)}$ under the isomorphism
    \[\hom(F(A),F(A))\cong \hom(A,F'F(A)) \cong \hom(G(A),F(A))\]
    for $\alpha:A\to B$ it will induce the commutative diagram
    \[
    \begin{tikzcd}
        \hom_{\mathcal{C'}}(F(A),F(A))\arrow[d]\arrow[r,"\cong"]& \hom_{\mathcal{C}}(A,F'F(A))\arrow[d]\arrow[r,"\cong"]& \hom_{\mathcal{C'}}(G(A),F(A))\arrow[d] \\
        \hom_{\mathcal{C'}}(F(A),F(B))\arrow[r,"\cong"]&\hom_{\mathcal{C}}(A,F'F(B))\arrow[r,"\cong"] & \hom_{\mathcal{C'}}(G(A),F(B)) \\
        \hom_{\mathcal{C'}}(F(B),F(B))\arrow[u]\arrow[r,"\cong"]&\hom_{\mathcal{C}}(B,F'F(B))\arrow[r,"\cong"]\arrow[u] & \hom_{\mathcal{C'}}(G(B),F(B))\arrow[u] 
    \end{tikzcd}
    \]
    where we may know $\theta(B)G(\alpha) = F(\alpha)\theta_A$ and hence $\theta$ is a natural transformation, similarly, define $\theta':F\to G$ and we will have
    \[
    \begin{tikzcd}
        \hom_{\mathcal{C'}}(F(A),F(A))\arrow[d]\arrow[r,"\cong"]& \hom_{\mathcal{C}}(A,F'F(A))\arrow[d]\arrow[r,"\cong"]& \hom_{\mathcal{C'}}(G(A),F(A))\arrow[d] \\
        \hom_{\mathcal{C'}}(F(A),G(A))\arrow[r,"\cong"]&\hom_{\mathcal{C}}(A,F'G(A))\arrow[r,"\cong"] & \hom_{\mathcal{C'}}(G(A),G(A)) \\ 
    \end{tikzcd}
    \]
    which is induced by $\theta'(A)$ and then $\theta'(A)\theta(A) = 1_G(A)$ and we are done.

    \begin{definition}
        (Direct limits)\par
        Let $\Lambda,\mathcal{C}$ categories and $\Lambda$ is small, i.e. its objects form a set. Given a functor $\lambda \mapsto M_{\lambda}$ from $\Lambda$ to $\mathcal{C}$, its direct limit denoted with $\varinjlim M_{\lambda}$ is defined to be the object of $\mathcal{C}$ universal among objects $P$ equipped with maps $\beta_{\mu}:M_{\mu} \to P$ what are compatible with the transition map $\alpha_{\mu}^{\kappa}:M_{\kappa} \to M_{\mu}$, i.e. there is a unique map $\beta$ such that all the diagrams
        \[
        \begin{tikzcd}
            M_{\kappa}\arrow[r,"\alpha_{\mu}^{\kappa}"]\arrow[d,"\beta_{\kappa}"] & M_{\mu}\arrow[r,
            "\alpha_{\mu}"]\arrow[d,"\beta_{\mu}"] & \varinjlim M_{\lambda}\arrow[d,"\beta"] \\
            P\arrow[r,"1_P"] & P\arrow[r,"1_P"] & P
        \end{tikzcd}
        \]
        where $\lambda\mapsto M_{\lambda}$ is often called a direct system. We know the limit is determined up to unique isomorphism.\par
        We say $\mathcal{C}$ has direct limits indexed by $\Lambda$ if for every functor $\lambda \mapsto M_{\lambda}$, the direct limit exists. We say that $\mathcal{C}$ has direct limits if it has direct limites indexed by every small category.\par
        Given a functor $F:C\to C'$, note that a functor  $\lambda\mapsto M_{\lambda}$ from $\Lambda$ to $\mathbb{C}$ yields a functor from $\Lambda$ to $\mathcal{C}'$. Furthermore, whenever the corresponding two direct limits exist, the maps $F(\alpha_{\mu}):F(M_{\mu}) \to F(\varinjlim M_{\lambda})$ induce a canonical map
        \[\phi_F:\varinjlim F(M_{\lambda}) \to F(\varinjlim M_{\lambda})\]
        If $\phi_F$ is always an isomorphism, we say $F$ preserves direct limits.
    \end{definition}

    \begin{proposition}
        Assume $\mathcal{C}$ has direct limits indexed by $\Lambda$. Then, given a natural transformation from $\lambda \mapsto M_{\lambda}$ to $\lambda \mapsto N_{\lambda}$, universality yields unique commutative diagrams
        \[
        \begin{tikzcd}
            M_{\mu}\arrow[r]\arrow[d] & \varinjlim M_{\lambda}\arrow[d] \\
            N_{\mu}\arrow[r] & \varinjlim N_{\lambda} 
        \end{tikzcd}
        \]
    \end{proposition}
    \Pf\par
        We know 
        \[\theta(\mu):M_{\mu} \to N_{\mu}, \theta(\mu)\alpha^{\lambda}_{\mu} = \beta^{\lambda}_{\mu}\theta(\lambda)\]
        and hence consider
        \[
        \begin{tikzcd}
             M_{\lambda}\arrow[r]\arrow[d] & M_{\mu}\arrow[r]\arrow[d] & \varinjlim M_{\lambda}\arrow[d,"\alpha"] \\
             N_{\lambda}\arrow[r]\arrow[d] & N_{\mu}\arrow[r]\arrow[d] & \varinjlim N_{\lambda}  \\
             P\arrow[r,"="] & P\arrow[r,"="] & P \\
        \end{tikzcd}
        \]
    \begin{definition}
        (Functor category)\par
        The functor category $\mathcal{C}^{\Lambda}$, i.e. a category with objects to be the functors from $\Lambda$ to $\mathcal{C}$ and the maps are the natrual transformation, then $\varinjlim$ yields a functor from $C^{\Lambda}$ to $C$.\par
        The direct  limit functor is the left adjoint of the diagonal function $\Delta:\mathcal{C} \to \mathcal{C}^{\Lambda}$ which send $M$ to the constant functor $\Delta M$ which has the same value $M$ at every $\Lambda$ and $1_M$ at every map of $\Lambda$; for $\gamma:M\to N$ it caarries $\gamma$ to $\Delta \gamma: \Delta M \to \Delta N$ which has the same value $\gamma$ at every $\lambda$.
    \end{definition}
    \Pf\par
        By proposition 1.6.2. we assume $\lambda\mapsto M_{\lambda},\lambda\mapsto N_{\lambda}$ and $\theta$ a natural transformation, then
        \[\varinjlim(\theta): \varinjlim M_{\lambda} \to \varinjlim N_{\lambda}\]
        which is uniquely determined.\par
        Notice
        \[\varinjlim: \mathcal{C}^{\Lambda} \to \mathcal{C},\quad \Delta: \mathcal{C} \to \mathcal{C}^{\Lambda}\]
        and we want to check
        \[\hom (\varinjlim (\lambda\mapsto M_{\lambda}), N) \cong \hom(\lambda\mapsto M_{\lambda},\Delta N)\]
        assume $\gamma: \varinjlim (\lambda\mapsto M_{\lambda}) \to N$ and then we would like $\gamma \mapsto \Delta \gamma$ is an isomorphism, which is obviously an injection and assume $\delta:\lambda\mapsto M_{\lambda} \to \Delta N$ where we know $\delta(\lambda):M_{\lambda} \to N$ which satisfies some commutative diagram and hence there exists a unique $\gamma: \varinjlim (\lambda\mapsto M_{\lambda}) \to N$.

    \begin{definition}
        (Coproduct)\par
        Let $\mathcal{C}$ be a category, $\Lambda$ a set and $M_{\lambda}$ an object for each $\lambda\in\Lambda$. The coproduct $\prod_{\lambda\in\Lambda} M_{\lambda}$ is defined as the object of $\mathcal{C}$ universal among objects $P$ equipped with a map $\beta_{\mu}:M_{\mu} \to P$ and the maps $\iota_{\lambda}: M_{\lambda} \to \prod M_{\lambda}$ is call the inclusions.\par
        If $\Lambda$ is empty then $B$ is an object with a unique map $\beta$ to other $P$ and such $B$ is called an initial object.
    \end{definition}

    \begin{definition}
        (Coequalizers)\par
        Let $\alpha,\alpha':M \to N$ their coequalizer is the object universal among $P$ with $\eta: N\to P$ such that $\eta\alpha = \eta\alpha'$.
    \end{definition}

    \begin{lemma}
        A category has direct limits iff it has coproducts and coqualizers. If a category has direct limits, then a functor preserves them iff it preserves coproduct and coequalizers.
    \end{lemma}
    \Pf\par
        Let $\Lambda \mapsto M_{\lambda}$ where $\hom(\mu,\nu)$ is empty for any $\mu \neq \nu$ and then the corresponding direct limit is the coproduct. For $M,N\in\mathcal{C}$ and two morphsims, then the inclusion of them two is a small category and the direct limit will be the coequalizer. If $F$ preserves direct limits, since we have shown that coproduct and coequalizer is special direct limits and we are done.\par
        Conversely, if $\mathcal{C}$ has coproducts and coequalizers. Assume $\Lambda$ a small category and $\lambda \mapsto M_{\lambda}$ a functor, let $\Sigma$ all transition maps and for each  $\sigma = \alpha^{\lambda}_{\mu} \in \Sigma$, set $M_{\Sigma} := M_{\lambda}$ and let $M:= \prod M_{\sigma}$ and $N = \prod M_{\lambda}$, for each $\sigma$, there are two maps $M_{\sigma} \to N$ which is $\iota_{\lambda}$ and the composition $\iota_{\mu}\alpha_{\mu}^{\lambda}$, then let $C$ be the coequalizer of corresponding maps $\alpha,\alpha':M\to N$ aand $\eta: N \to C$ the insertion. So if $\beta_{\lambda}: M_{\lambda} \to P$ compatible with the transition maps, then there is a unique $\beta: N \to P$  such that $\beta\iota_{\lambda} = \beta_{\lambda}$ and hence $\beta\alpha = \beta\alpha'$ and we are done.\par
        If $F$ preserves coproduct and coeqqualizers, then $F$ preserves the construction and we are done.

    \begin{theorem}
        The categories $R$-module and sets have direct limits.
    \end{theorem}

    \begin{theorem}
        Every left adjoint $F:\mathcal{C}\to \mathcal{C'}$ preserves direct limits.
    \end{theorem}

    \begin{proposition}
        Let $\mathcal{C}$ be a category, $\Lambda$ and $\Sigma$ small categories. Assume $\mathcal{C}$ has direct limits indexed by $\Sigma$. Then the functor category $\mathcal{C}^{\Lambda}$ does too.
    \end{proposition}

    \begin{theorem}
        Let $\mathcal{C}$ be a category with direct limits indexed by small categories $\Sigma$ and $\Lambda$. Let $\sigma\mapsto (\lambda\mapsto M_{\sigma \lambda})$ be a functor from $\Sigma$ to $\mathcal{C}^{\Lambda}$. Then
        \[\varinjlim_{\sigma} \varinjlim_{\lambda} M_{\sigma\lambda} = \varinjlim_{\lambda} \varinjlim_{\sigma}  M_{\sigma\lambda}\]
    \end{theorem}
    \begin{corollary}
        Let $\Lambda$ be a small category, $R$ a ring, and $\mathcal{C}$ is sets or $R$-modules. Then functor $\varinjlim:\mathcal{C}^{\Lambda} \to \mathcal{C}$ preserves coproduces and coequalizers.
    \end{corollary}
\subsection{Tensor Products}

\begin{definition}
    (Bilinear maps)\par
    Let $R$ be a ring and $M,N,P$ modules. We call a map $\alpha: M\times N \to P$ bilinear if it is lienarin each variable. Denote the set of all these maps by $\text{Bil}_R(M,N;P)$, it is clearly an $R$-module with sum and scalar multiplication performed valuewise.
\end{definition}

\begin{definition}
    (Tensor product)\par
    Let $R$ be a ring and $M,N$ modules. Their tensor product denoted $M\otimes_R N$ is constructed as the quotient of the free module $R^{\oplus (M\times N)}$ modulo the submodule generated by the following elemants, where $(m,n)$ stands for the standard basis element $e_{(m,n)}$:
    \[
    (m+m',n)-(m,n)-(m',n), (m,n+n')-(m,n) - (m,n'), (xm,n), (m,xn)-x(m,n)
    \]
    and the above construction yields a canonical bilinear map
    \[
    \beta:M\times N \to M \otimes N
    \]
    and set $m\otimes n:=\beta(m,n)$
\end{definition}

\begin{theorem}
    (UMP of tensor product)\par
    Let $R$ be a ring, $M,N$ modules. Then $\beta:M\times N \to M\otimes N$ is the universal bilinear map with source $M\times N$; in fact, $\beta$ induces a module isomorphism
    \[\theta:\hom_R(M\otimes_R N, P) \cong \text{Bil}_R(M,N;P)\]
\end{theorem}

\begin{corollary}
    (Bifunctoriality)\par
    Let $R$ be a ring, $\alpha:M\to M'$ and $\alpha':N\to N'$ module homomorphisms. Then there is a canonical commutative diagram:
    \[
    \begin{tikzcd}
        M\times N\arrow[r,"\alpha\times\alpha'"]\arrow[d,"\beta"] & M'\times N'\arrow[d,"\beta'"]\\
        M\otimes N\arrow[r, "\alpha\otimes\alpha'"] & M'\otimes N' \\
    \end{tikzcd}
    \]
\end{corollary}
\Pf\par
    Notice
    \[
    (\alpha\otimes \alpha')(m\otimes n) = \alpha m\otimes \alpha'n
    \]

\begin{proposition}
    Let $R$ be a ring, $M$ and $N$ modules,
    \begin{itemize}
        \item Then the switch map $(m,n)\mapsto (n,m)$ induces an isomorphism
        \[M\otimes_R N = N\otimes_R M\]
        \item The multiplication on $M$ indcues an isomorphism
        \[R\otimes_R M = M\]
    \end{itemize}
\end{proposition}
\Pf\par
    The switch map induces an isomorphism between $M\otimes_RN = N\otimes_R M$.\par
    Define $\beta:R\times M \to M$ by $\beta(x,m):= xm$, then $\beta$ is bilinear and we have
    for any $\alpha:R\times M\to P$, define $\gamma:M\to P$ by $\gamma(m) = \alpha(1,m)$ and then $\alpha = \gamma\beta$, where $\gamma$ is unique since $\beta$ surjective and hence $M\cong R\otimes M$ since
    \[
    \begin{tikzcd}
        R\times M\arrow[r,"\beta'"]\arrow[d]\arrow[rd,"\beta"] & P \\
        R\otimes M\arrow[ru,"\beta''"] & M \arrow[u,"\gamma"]\\
    \end{tikzcd}
    \]
    let $P$ be $M$ and $R\otimes M$ and we are done.

\begin{definition}
    Let $R$ and $R'$ be rings. An abelian group $N$ is an $(R,R')$-bimoudle if it is both an $R$-module and an $R'$-module if $x(x'n) = x'(xn)$ for all $x\in R,x'\in R'$ and $n\in N$.
\end{definition}

\subsection{Flatness}

\begin{lemma}
    Let $R$ be a ring, $\alpha:M\to N$ a homomorphism of modules. Then there is a commutative diagram with two short exacct sequences involving $N'$
    \[
    \begin{tikzcd}
        0\arrow[r] & M'\arrow[r] & M\arrow[rd,"\alpha'"]\arrow[rr,"\alpha"] & & N\arrow[r]& N''\arrow[r] & 0 \\
          & & 0\arrow[r] & N'\arrow[r]\arrow[ru,"\alpha''"]\arrow[ru] & 0 \\      
    \end{tikzcd}
    \]
    iff $M' = \ker\alpha$ and $N' = \text{Im}\alpha$ and $N'' = \text{Coker}\alpha$. 
\end{lemma}

\begin{definition}
    (Exact Functors)\par
    Let $R$ be a ring , $R'$ an algebra, $F$ a linear functor from (($R$-mod)) to (($R'$-mod)). Call $F$ faithful if the associated map
    \[
    \hom_R(M,N) \to \hom_{R'}(FM,FN)
    \]
    is injective, or equivalently, if $F\alpha = 0$ implies $\alpha = 0$. Call $F$ exact if it preserves exact sequences, left exact if it preserves kernels and right exact if it preserves cokernels.
\end{definition}

\begin{proposition}
    Let $R$ be a ring, $R'$ an algebra, $F$ an $R$-linear functor from (($R$-mod)) to (($R'$-mod)). Then the following conditions are equivalente
    \begin{itemize}
        \item $F$ is exact
        \item $F$ preserves short exact sequences
        \item $F$ preserves kernels and surjections.
        \item $F$ preserves cokernels and injections
        \item $F$ preserves kernels and images
    \end{itemize}
\end{proposition}
\Pf\par
    (1) implies (2),(3),(4) is trivial. (3) implies (2) and (4) implies (2) are trivial. (2) implies (5) by lemma and assume (5), let $M'\to M \to M''$ exact, then $\ker(\beta) = \text{Im}(\alpha)$ and then $\ker(F(\beta)) = F(\ker(\beta)) = F(\text{Im}(\alpha)) = \text{Im}F\alpha$ and we are done.

\begin{definition}
    (Flatness)\par
    We say an $R$-module $M$ is flat over $R$ or is $R$-flat if $M\otimes_R \cdot$ is exact. It is equivalent with that $M\otimes_R \cdot$ preserve injection since it preserves cokernels.\par
    We say  $M$ is faithfully if $M\otimes_R \cdot$ is exact and faithful.\par
    We say an $R$-algebra is falt or faithfully flat if it is so as an $R$-module.
\end{definition}

\subsection{Cayley-Hamilton Theorem}

\begin{theorem}
    (Cayley-Hamilton Theorem)\par
    Let $R$ be a ring, and $M:= (a_{i,j})$ with $a_{i,j} \in R$, Then characteristic polynomial of $M$ is
    \[P_M(T) := T^n + a_1T^{n-1}+\cdots + a_n := \det(TI_n - M)\]
    Let $A$ be an ideal. If $a_{ij} \in A$ for all $i,j$, then $a_k \in A^k$ for all $k$.\par
    The Cayley-Hamilton Theorem asserts that in the ring of matrices,
    \[P_M(M) = 0\]
\end{theorem}

\subsection{Localization}

\begin{definition}
    (Localization)\par
    Let $R$ be a ring, and $S$ a multiplicative subset. Define a relation on $R\times S$ by $(x,s) \sim (y,t)$ if there is a $u\in S$ such that $xtu = ysu$, which is an quivalence relation. Denote $S^{-1}R$ the set of equivalence classes, and by $x/s$ the class of $(x,s)$ and defined $x/s \cdot y/t:= xy/st$ and $x/s+y/t = (tx+sy)/st$, and then $S^{-1}R$ wil be a ring, which is called the localization at $S$. $\phi_S:R\to S^{-1}R$ by $\phi_S(x):= x/1$.
\end{definition}

\section{Fields and Galois Theory}

\subsection{Definitions and Results}

\begin{definition}
    A field is a set $F$ with binary operations $+$ and $\cdot$ such that
    \begin{itemize}
        \item $(F,+)$ is a commutative group
        \item $(F^{\times},\cdot)$ where $F^{\times} = F - \{0\}$ is a commutative group
        \item the distributive law holds
    \end{itemize}
\end{definition}

\begin{lemma}
    A nonzero commutative ring $R$ is a field iff it has no ideals other than $(0)$ and $R$.
\end{lemma}

\begin{definition}
    An $F$-algebra for a field $F$ is finite if it is a finite-dimensional $F$-vector space.
\end{definition}

\begin{definition}
    (Characteristic of a Field)\par
    Consider $Z\to F$ by $n\mapsto n 1_F$, if the kernel of this map is $(0)$, then there exists $Q\hookrightarrow F$ and we say it has characteristic zero.\par
    If the kernel is not zero, then the smallest integer in the kernel has to be a prime $p$ and we know $F_p\hookrightarrow F$ and we call it has caracteristic $p$. A field isomorphic to $F_p$ or $Q$ is called a prime field.
\end{definition}

\begin{definition}
    (Frobenius endomorphism)\par
    Assume $R$ a commutative ring has characteristic $p$ if it contains a prime field of characteristic $p$ as a subring, then the prime field is unique and contains $1_R$, it is easy to qcheck that $(a+b)^p = a^p + b^p$ for any $a,b\in R$ if $p$ is nonzero and hence $a\mapsto a^p$ us a homomorphism and it is called the frobenius endomorphism of $R$. The charaacteristic exponent of a field $F$ is 1 if $F$ has characteristic $0$ and $p$ if $F$ has characteristic $p\neq 0$.
\end{definition}

\begin{proposition}
    (Gauss's Lemma)\par
    Let $f(X) \in \mathbb{Z}[X]$. If $f(X)$ factors nontrivially in $\mathbb{Q[X]}$, then it factors nontrivially in $\mathbb{Z}[X]$.
\end{proposition}

\begin{proposition}
    If $f\in \mathbb{Z}[X]$ is monic, then every monic factor of $f$ in $\mathbb{Q}[X]$ lies in $\mathbb{Z}[X]$.
\end{proposition}

\begin{proposition}
    (Eisenstein's Criterion)\par
    Let $f = a_m X^m + a_{m-1}X^{m-1}+\cdots + a_0, a_i \in \mathbb{Z}$
    suppose that there is a prime number $p$ such that
    \begin{itemize}
        \item $p$ does not divide $a_m$
        \item $p$ divides $a_{m-1},\cdots,a_0$
        \item $p^2$ does not divide $a_0$
    \end{itemize}
    then $f$ is irreducible in $\mathbb{Q}[X]$.
\end{proposition}

\subsubsection{Extensions}

\begin{definition}
    (Extensions)\par
    Let $F$ be a field. An \textbf{extension} of $F$ is field containing $F$ as a subfield. An extension $E$ of $F$ is an $F$-vector space, whose dimension is called the \textbf{degree} $[E:F]$ of $E$ over $F$. An extension is said to be finite if its degree is finite.\par
    When $E$ and $E'$ are extensions of $F$, an $F$-homomorphism $E\to E'$ is a homomorphism $\phi:E\to E'$ such that $\phi|_F\circ id|_F = id_F$ and an $F$-isomorphism is a bijective $F$-homomorphism.
\end{definition}

\begin{proposition}
    Consider fields $F\supset E \supset F$. Then $L/F$ is of finite degree if and only if $L/E$ and $E/F$ are both of finite degree, in which case
    \[[L:F] = [L:E][E:F]\]
\end{proposition}
\Pf\par
    To see the sufficiency, obviously $[L:F] \geq [L:E]$ and assume $\{l_i\}_{i=1}^m$ a basis of $L$ as an $F$-vector space and then $E$ as an $F$-vector space will satisfy that $[E:F] \leq [L:F]$. Assume $\{e_i\}_{i=1}^k$ and $\{l'_j\}_{j=1}^r$ are relatively bases of $E$ as an $F$-vector space and $L$ as an $E$-space. Then we may know that $\{e_il'_j\}$ will generate $L$ and will become a basis since if
    \[
    \sum\limits_{1\leq i \leq k,1\leq j \leq r} f_{ij}e_il_j' = 0 
    \]
    will implies that $\sum\limits_{i=1}^k f_{ij}e_i = 0$ for each $j, 1\leq j\leq r$ and then $f_{ij} = 0$ for any $i,j$ and we are done.

\begin{definition}
    (Generated subring)\par
    Let $F$ be a subfield of a field $E$ and $S$ a subset of $E$. The intersection of all subrings of $E$ containing $F$ and $S$ is called the subring of $E$ \textbf{generated by} $F$ and $S$ and denoted by $F[S]$.
\end{definition}

\begin{lemma}
    The ring $F[S]$ consists of the elements of $E$ that can be expressed as $F$-linear combanation of finite product of elements in $S$ (including $0$ elements, i.e. $1_F$).
\end{lemma}

\begin{lemma}
    Let $R$ be a finite $F$-algebra. If $R$ is an integral domain, then it is a field.
\end{lemma}
\Pf\par
    Let $\alpha \in R$ nonzero, and consider $x\to \alpha x$ which is an injective linear map and hence surjective since $R\to R$ finite-dimensional and we are done.

\begin{definition}
    (Generated subfield)\par
    Let $F$ be a subfield of a field $E$ and $S$ a subset of $E$. The intersection of all subfields of $E$ containing $F$ and $S$ is called the subfield of $E$ \textbf{generated by} $F$ and $S$ and denoted by $F(S)$,which is the field of fractions of $F[S]$.
\end{definition}

\begin{definition}
    (Simple extension and composite)\par
    An extension $E$ of $F$ is said to be \textbf{simple} if $E = F(\alpha)$ for some $\alpha \in E$. Let $F$ and $F'$ be subfields of a field $E$. We call the intersection of subfields of $E$ containing both $F$ and $F'$ as the \textbf{composite} of $F$ and $F'$ in $E$. 
\end{definition}

\begin{proposition}
    For a monic irreducible polynomial $f(X)$ of degree $m$ in $F[X]$, then $F[x] := F[X]/(f)$ is a field of degree $m$ over $F$.
\end{proposition}

\begin{definition}
    (Stem fields)\par
    Let $f$ be a monic irreducible polynomial in $F[X]$. A pair $(E,\alpha)$ cconsisting of an extension $E$ of $F$ and an $\alpha \in E$ is called a \textbf{stem field} for $f$ if $E = F[\alpha]$ and $f(\alpha) = 0$, which is $F$-isomorphic to $(F[X]/(f),x)$.
\end{definition}

\subsubsection{Algebraic and Transcendental Elements}

\begin{definition}
    (Algebraic and Transcendental Elements)\par
    Let $F$ be a field and $E$ an integral domain containing $F$ as a subring. An element $\alpha$ of $E$ defines a homomorphism $f(X)\mapsto f(\alpha): F[X] \to E$.\par
    If the kernel of the map is zero, then we call $\alpha$ \textbf{transcendental} over $F$.\par
    If the kernel is nonzero, then we say $\alpha$ is \textbf{algebraic} over $F$. We call the monic, irreducible polynomial $f$ generating the kernel the \textbf{minimal polynomial} of $\alpha$ over $F$, and then $F[\alpha]$ is a stem field for $f$.
\end{definition}

\begin{definition}
    (Algebraic extension)\par
    An extension $E$ of $F$ is said to be \textbf{algebraic} if every element of $E$ is algebraic over $F$, otherwise it is said to be \textbf{transcendental}.
\end{definition}

\begin{proposition}
    Let $E\supset F$ be fields. If $E/F$ is finite, then $E$ is algebraic and finitely generated over $F$; conversely, if $E$ is generated over $F$ by a finite set of algebraic elements, then it is of finite degree over $F$.
\end{proposition}
\Pf\par
    If $\alpha$ is transcendental over $F$, then we know $1,\alpha,\alpha^2,\cdots$ are linearly independent over $F$, which is a contradiction. And if $E = F$, then $E$ is generated by the empty set. Or there is an element in $E-F$ and we will have
    \[[F[\alpha_1]:F] < [F[\alpha_1,\alpha_2]:F]<\cdots<[E:F]\]
    which means $E = F[\alpha_1.\alpha_2,\cdots,\alpha_n]$ for some integer $n$ and $\alpha_i \in E$.\par
    Notice $F[\alpha_1]$ is finite generated since $\alpha_1$ is algebraic and hence $F[\alpha_1] = F(\alpha_1)$, which means $F(\alpha_1)/F$ is finite. Then notice $\alpha_2$ is algebraic over $F(\alpha_1)$ and repeating the argument.

\begin{corollary}
    Consider fields $L\supset E \supset F$. If $L$ is algebraic over $E$ and $E$ is algebraic over $F$, then $L$ is algebraic over $F$.
\end{corollary}
\Pf\par
    Consider $l\in L$ is a root of $\sum\limits_{i=0}^m a_iX^i$ and then $F[a_0,\cdots,a_m]$ is finite over $F$ and $F[a_0,\cdots,a_m,l]$ is finite over $F$ and hence $l$ is algebraic oveer $F$.

\begin{proposition}
    Let $F$ be a field and $R$ an integral domain containing $F$ as a subring. If $R$ is generated as an $F$-algebra by elements algebraic over $F$, then it is a field algebraic over $F$.
\end{proposition}
\Pf\par
    For any $r\in R$, there exists $\{\alpha_i\}_{i=1}^m$ such that $r \in F[\alpha_1,\cdots,\alpha_m]$ (as a fraction) and then since for any $\alpha_i$, there exists $a_j\in F$ such that $\alpha_i^{m} = a_0 + a_1\alpha_i+\cdots+a_m\alpha_i^{m-1}$ and we may know that $F[\alpha_1,\cdots,\alpha_m]$ is finite and hence algebraic, which means $r$ is algebraic over $F$.

\subsubsection{Algebraically Closed Fields}

\begin{definition}
    Let $F$ be a field. A polynomial is said to \textbf{split} in $F[X]$ if it is a product of polynomials of degree at most $1$ in $F[X]$.
\end{definition}

\begin{proposition}
    For a field $\Omega$, the following statemetns are equivalent:\par
    \begin{itemize}
        \item Every nonconstant polynomial in $\Omega[X]$ splits in $\Omega[X]$
        \item Every nonconstant polynomial in $\Omega[X]$ has at least one root in $\Omega$
        \item The irreducible polynomials in $\Omega[X]$ are those of degree $1$
        \item Every field of finite degree over $\Omega$ equals $\Omega$.
    \end{itemize}
\end{proposition}
\Pf\par
    (a) to (b) to (c) are obvious.\par
    (c) to (a) by UFD. (c) to (d), consider $E$ a finite extension and hence algebraic, for $\alpha \in E$ the minimal polynomial of $\alpha$ has degree $1$ and we are done.\par
    (d) to (c) consider $\Omega[X]/(f)$ and its degree has to be $1$ and we are done.

\begin{definition}
    (Algebraic Closure)\par
    A field $\Omega$ is \textbf{algebraically closed} if it satisfies the equivalent statements above. A field $\Omega$ is an \textbf{algebraic closure} of a subfield $F$ if it is algebraically closed and algebraic over $F$.
\end{definition}

\begin{proposition}
    If $\Omega$ is algebraic over $F$ and every polynomial $f$ splits in $\Omega[X]$, then $\Omega$ is algebraically closed.
\end{proposition}
\Pf\par
    Let $f\in \Omega[X]$ and we want to show $f$ has a root in $\Omega$. Since $f$ has a root $\alpha$ insome finite extension $\Omega'$ of $\Omega$ and consider
    \[F\subset F[a_0,\cdots,a_n]\subset[a_0,\cdots,a_n,\alpha]\]
    which is finite since they are all generated by finite algebraic elements and hence $\alpha$ is algebraic over $F$ and hence it is a root of some polynomial in $F$ and then $\alpha \in \Omega$ and we are done.

\begin{proposition}
    Let $F$ be a field and $\Omega$ an integral domain containing $F$ as a subring. Then $\bar{F}:= \{\alpha \in \Omega, \alpha\text{ algebraic over }F\}$ is a field, which is called the algebraic closure of $F$ in $\Omega$.
\end{proposition}
\Pf\par
    Notice $F[\alpha,\beta]$ is finite over $F$.

\begin{corollary}
    Let $\Omega$ be an algebraically closed field. For any subfield $F$ of $\Omega$, the algebraic closure $E$ of $F$ in $\Omega$ is an algebraic closure of $F$.
\end{corollary}
\Pf\par
    For $f\in F[X]$ we know it splits in $\Omega[X]$ and is has its roots in $E$, so splits in $E[X]$ and we are done.

\subsection{Splitting Fields; Multiple Roots}

\begin{proposition}
    Let $F(\alpha)$ be a simple extension of $F$ and $\Omega$ a second extension of $F$.\par
    \begin{itemize}
        \item Suppose $\alpha$ is transcendental over $F$. For every $F$-homomorphism $\phi:F(\alpha) \to \Omega$, $\phi(\alpha)$ is transcendental over $F$, and the map $\phi\mapsto \phi(\alpha)$ defines a one-to-one correspondence
        \[\{F\text{-homomorphisms } F(\alpha) \to \Omega \}\leftrightarrow \{\text{elements of } \Omega \text{ transcendental over }F\}\]
        \item Suppose $\alpha$ is algebraic over $F$, and let $f(X)$ be its minimal polynomial. For every $F$-homomorphism $\phi:F[\alpha]\to \Omega$, $\phi(\alpha)$ is a root of $f(X)$ in $\Omega$, and the map $\phi \mapsto \phi(\alpha)$ defines a one-to-one correspondence
        \[\{F\text{-homomorphisms } F(\alpha) \to \Omega \}\leftrightarrow \{\text{roots of } f \text{ in }\Omega\}\]
        In particular, the number of such maps is the number of distinct roots of $f$ in $\Omega$.
    \end{itemize}
\end{proposition}
\Pf\par
    (a) For an $F$-homomorphism, since $F[\alpha]$ is isomorphic to the polynomial ring with symbol $\alpha$, then consider $\phi(\alpha) = \gamma$ and since $\phi$ is defined on $F(\alpha)$, which implies that $\gamma$ is transcendental over $F$. By the way, only notice that $\phi(\alpha) = \gamma$ transcendental will extend to a unique homomophism $F(\alpha) \to \Omega$.\par
    (b) Only need to check the necessity, if $\gamma \in \Omega$ a root of $f(X)$, then consider $F[X] \to \Omega: g(X) \mapsto g(\gamma)$, which factors through $F[X]/(f(X))$ which is isomorphic to $F[\alpha]$ and hence $\phi$ sends $\alpha$ to $\gamma$.

\begin{proposition}
        Let $F(\alpha)$ be a simple extension of $F$ and $\phi_0:F\to \Omega$ a homomorphism from $F$ into a second field $\Omega$.\par
    (a) If $\alpha$ is transcendental over $F$, then the map $\phi \mapsto \phi(\alpha)$ defines a one-to-one correspondence
    \[
    \{\text{extensions }\phi:F(\alpha) \to \Omega\text{ of }\phi_0\} \leftrightarrow \{\text{elements of }\Omega\text{ transcendental over }\phi_0(F)\}
    \]\par
    (b) If $\alpha$ algebraic over $F$, with minimal polynomial $f(X)$, then the map $\phi \mapsto \phi(\alpha)$ defines a one-to-one correspondence
    \[
    \{\text{extensions }\phi:F[\alpha] \to \Omega\text{ of }\phi_0\} \leftrightarrow \{\text{roots of }\phi_0f\text{ in }\Omega\}
    \]
    In particular, the number of such maps is the number of distinct roots of $\phi_0f$ in $\Omega$. 
\end{proposition}
    
\begin{definition}
    Let $f$ be a polynomial with coefficients in $F$. A field $E$ containing $F$ is said to \textbf{split} $f$ if $f$ splits in $E[X]$ and we call $E$ a \textbf{splitting} or \textbf{root field} for $f$ if it is generated by the roots of $f$.
\end{definition}

\begin{proposition}
    Every polynomial $f\in F[X]$ has a splitting field $E_f$ and $[E_f:F] \leq (\deg f)!$.
\end{proposition}
\Pf\par
    Let $F_1 = F[\alpha_1]$ be a stem field for some monic irreducible factor of $f$ in $F[X]$ and let $F_2 = F_1[\alpha_2]$ be a stem field for some monic irreducible factor of $f(X)/(X-\alpha_1)$ and continuing, we will have a splliting field $E_f$ where $[F_{k+1}:F_k] \leq n-k, F_0 = F$ and we are done.

\begin{proposition}
    Let $f\in F[X]$. Let $E$ be an extension of $F$ generated by the roots of $f$ in $E$ and $\Omega$ an extension of $F$ splitting $f$. There exists an $F$-homomorphism $\phi:E\to \Omega$ and the number of such homomorphisms is at most $[E:F]$ an equivalents $[E:F]$ if $f$ has distinct roots in $\Omega$.
\end{proposition}
\Pf\par
    Suppose $f$ monic. Assume $f = \prod (X-\beta_i) \in \Omega[X]$ and $L$ a subfield of $\Omega$ containing $F$, $g$ a monic factor if $f$ in $L[X]$. We know $g|f$ in $\Omega[X]$ and hence a product of some $X-\beta_i$, which means $g$ splits in $\Omega$ and has distinct roots if $f$ does.\par
    $E = F[\alpha_1,\cdots,\alpha_m]$ with $\alpha_i \in E$ roots of $f$ and we know the minimal polynomial of $\alpha_1$ is an irreducible $f_1|f$. Then we know $f_1$ splits in $\Omega$ by letting  $L=F$ with distinct roots if $f$ have. Then we know the number of $F$-homomorphism $\phi_1:F[\alpha_1] \to \Omega$ is the number of distinct roots of $f_1$, whose degree is $[F[\alpha_1]:F]$ with equality when $f$ has distinct roots in $\Omega$. The minimal polynomial of $\alpha_2$ over $F[\alpha_1]$ is an irreducible $f_2$ in $F[\alpha_1][X]$, then let $L = \phi_1F[\alpha_1]$ and $g = \phi_1f_2$ which splits in $\Omega$ and its roots are distinct if the roots of $f$ are and each $\phi_1$ extends to a homomorphism $\phi_2:F[\alpha_1,\alpha_2] \to \Omega$ with at most $[F[\alpha_1,\alpha_2]:F[\alpha_1]]$ with equality when $f$ has distinct roots and continuing, we are done.

\begin{corollary}
    If $E_1$ and $E_2$ are both spliiting field for $f$, then every $F$-homomorphism $E_1 \to E_2$ is an isomorphism. In particular, any two splitting fields for $f$ are $F$-isomorphic.
\end{corollary}
\Pf\par
    Notice that every $F$-homomorphism $E_1 \to E_2$ is injective, which is since it is a field homomorphism and then we know $[E_1:F] \leq [E_2:F]$ and hence $[E_1:F] = [E_2:F]$ which means that $E_1 \cong E_2$ for each homomorphism.

\begin{corollary}
    Let $E$ and $L$ be extension of $F$, with $E$ finite over $F$. The number of $F$-homomorphisms $E\to L$ is at most $[E:F]$.
\end{corollary}
\Pf\par
    Let $E= F[\alpha_1,\cdots,\alpha_m]$ and let $f\in F[X]$ be the product of the minimal polynomials (which has to exist) of $\alpha_i$ and hence $E$ is generated over $F$ by roots of $F$. Let $\Omega$ be a splitting field for $f$ as an element of $L[X]$. Then there exists an $F$-homomorphism $E\to \Omega$ and the number of such homomorphisms is at most $[E:F]$. For an $F$-homomorphism $E\to L$, it has to be able to regarded as an $F$-homophism since $\Omega$ is an $L$ extension.

\begin{proposition}
    Let $f$ and $g$ be polynomials in $F[X]$ and let $\Omega$ be an extension of $F$. If $r(X)$ is the gcd of $f$ and $g$ computed in $F[X]$, then it is also the gcd of $f$ and $g$ in $\Omega[X]$. In particular, distict monic irreducible polynomials in $F[X]$ do not acquire a common root in any extension of $F$.
\end{proposition}
\Pf\par
    Notice $r_F(X)|r_{\Omega}(X)$ and use the Euclid.

\begin{definition}
    (Multiplicity)\par
    Let $f\in F[X]$ and $f$ splits into linear factors
    \[f(X) = a \prod_{i=1}^r (X-\alpha_i)^{m_i},\quad a\in F,\quad \alpha_i\text{ distinct},\quad m_i\geq 1\]
    in $E[X]$ for some extension of $F$ and we say $\alpha_i$ is a root of $f$ of \textbf{multiplicity} $m_i$ in $E$, where $\{m_i\}$ is independent with the extension. We say $f$ \textbf{has a multiple root} when at least one $m_i >1$ and $f$ \textbf{has only simple roots} when $m_i = 1$.
\end{definition}
\Pf\par
    Consider $E$ and its subfield $F[\alpha_1,\cdots,\alpha_r]$, where $\{m_i\}$ keep unchanged and we may consider $E,E'$ all splitting fields of $f$ and then we know they are $F$-isomorphic.

\begin{definition}
    (Derivative)\par
    The \textbf{derivative} of a polynomial $f(X) = \sum a_iX^i$ is defined to be $f'(X) = \sum ia_iX^{i-1}$.
\end{definition}

\begin{lemma}
    A root of $f$ is multiple if and only if it is also a root of $f'$.
\end{lemma}

\begin{proposition}
    For a nonconstant irreducible polynomial $f$ in $F[X]$, the following are equivalent
    \begin{itemize}
        \item $f$ has a multiple root
        \item $gcd(f,f') \neq 1$
        \item $F$ has nonzero characteristic $p$ and $f$ is a polynomial in $X^p$
        \item all the roots of $f$ are multiple.
    \end{itemize}
\end{proposition}
\Pf\par
    (d) to (a), (a) to (b) trivial. For (b) to (c), as $f$ is irreducible and $\deg f' < \deg  f$, then $gcd(f,f') \neq 1$ implies that $f' = 0$ and hence $f = a_0 + \cdots + a_dX^d$ implies that $f' = a_1 + \cdots + ia_i X^{i-1} + \cdots + da_dX^{d-1}$ which is zero iff $F$ has characteristic $p \neq 0$ and $a_i = 0$ for all $i$ not divisible by $p$. (c) to (d) consider $f(X) = g(X^p)$ which implies $g = \prod (X-a_i)^{m_i}$ for some $p^{th}$ power $a_i$ and then $f(X) = g(X^p) = \prod (X^p - a_i)^{m_i} = \prod (X-\alpha_i)^{pm_i}$ for some $\alpha_i$.

\begin{proposition}
    The following conditions on a nonzero polynomial $f\in F[X]$ are equivalent:
    \begin{itemize}
        \item $gcd(f,f') = 1$ in $F[X]$
        \item $f$ has only simple roots.
    \end{itemize}
\end{proposition}

\begin{definition}
    (Separable)\par
    A polynomial is \textbf{separable} if it is nonzero and satisfies the equivalent conditions above.
\end{definition}

\begin{definition}
    A field $F$ is \textbf{perfect} if it has characteristic zero or it has characteristic $p$ and every element of $F$ is a $p^{th}$ power.
\end{definition}

\begin{proposition}
    A field $F$ is perfect if and only if every irreducible polynomial in $F[X]$ is separable.
\end{proposition}
\Pf\par
    If $F$ has characteristic zero, the statement is obvious. If $F$ has a nonzero characteristic, and $A$ is not a $p^{th}$ power, then $X^p - a$ is irreducible but not separable. Conversely, if every element of $F$ is a $p^{th}$ power, then every polynomial in $X^p$ is a $p^{th}$ power in $F[X]$ and hence not irreducible.\par
    To see $X^p - a$ is irreducible, consider $\alpha$ a root of $X^p - a$ in some extension, then we know $X^p - a = (X-\alpha)^p$ in the extension, and hence $(X-\alpha)^d$ is in $F[X]$ for some $d$, which means $d\alpha \in F$ and hence $\alpha \in F$, which is a contradiction.

\subsection{The Fundamental Theorem of Galois Theory}

\subsubsection{Galois Group}

\begin{definition}
    (Automorphism)\par
    Consider fields $E\supset F$. An $F$-isomorphism $E\to E$ is called an $F$-automorphism of $E$. The $F$-automorphisms of $E$ form a group, which we denote $\text{Aut}(E/F)$.
\end{definition}

\begin{proposition}
    Let $E$ be a splitting field of a separable polynomial $f$ in $F[X]$; then $\text{Aut}(E/F)$ has order $[E:F]$.
\end{proposition}
\Pf\par
    As $f$ separable, it has $\deg f$ distinct roots in $E$ and hence then we know that the number of $F$-homomorphisms $E\to E$ is $[E:F]$ and we are done.

\begin{definition}
    (Fixed field)\par
    When $G$ is a group of automorphisms of a field $E$, we set
    \[E^G = \text{Inv}(G) = \{\alpha \in E| \sigma \alpha = \alpha,\text{ for all }\sigma\in G\}\]
    which will be a subfield of $E$ and hence called the \textbf{fixed field} of $G$.
\end{definition}

\begin{theorem}
    Let $G$ be a finite group of automorphisms of a field $E$, then
    \[[E:E^G] \leq (G:1):=|G|\]
\end{theorem}
\Pf\par
    Let $F = E^G$ and let $G = \{\sigma_1,\cdots,\sigma_m\}$ with $\sigma_1$ identity. It suffices to show that every set $\{\alpha_1,\cdots,\alpha_n\}$ of elements of $E$ with $n>m$ is linearly dependent. Consider
    \[
    \sigma_i(\alpha_1)X_1 + \cdots \sigma_i(\alpha_n) X_n = 0
    \]
    will have nontrivial solutions in $E$ and hence we choose $(c_1,\cdots,c_n)$ with fewest possible nonzero elements and WLOG $c_1 \in E^G$ nonzero. If not all $c_i$ are in $F$, then $\sigma_k(c_i) \neq c_i$ for some $k \neq 1$ and then we will find
    $(c_1,,\sigma_k(c_2),\cdots,\sigma_k(c_i),\cdots)$
    is a solution and then we will obtain a solution with lest nonzero elements. So $c_1,\cdots,c_n \in E^G$ and we are done.

\begin{corollary}
    Let $G$ be a fintie group of automorphisms of a field $E$, then $G = \text{Aut}(E/E^G)$. 
\end{corollary}
\Pf\par
    As $G\subset \text{Aut}(E/E^G)$ and
    \[
    [E:E^G] \leq |G| \leq |\text{Aut}(E/E^G)| \leq [E:E^G]
    \]
    and hence $G = \text{Aut}(E/E^G)$.

\begin{definition}
    (Separable Extension)\par
    An algebraic extension $E/F$ is \textbf{separable} if the mininal polynomial of every element is separable; other wise, it is \textbf{inseparable}.
\end{definition}

\begin{proposition}
    An algebraic extension $E/F$ is separable if every irreducible polynomial in $F[X]$ having a root in $E$ is separable, and it is inseparable if $F$ is nonperfect and there is an element $\alpha$ of $E$ whose minimal polynomial is of the form $g(X^p)$ with $p$ the characteristic of $F$.
\end{proposition}

\begin{definition}
    (Normal Extension)\par
    An algebraic extension $E/F$ is \textbf{normal} if it is algebraic and the minimal polynomial of every element of $E$ splits in $E[X]$.
\end{definition}

Here is an extra useful proposition.

\begin{proposition}
    Let $\Omega/F$ be an extension of fields. If $\Omega$ is algebraic over $F$ and every nonconstant polynomial in $F[X]$ has a root in $\Omega$, then $\Omega$ is algebraically closeds.    
\end{proposition}

\begin{proposition}
    An algebraic extension $E/F$ is normal if every irreducible polynomial in $F[X]$ having one root in $E$ will split in $E[X]$.
\end{proposition}

\begin{proposition}
    Let $E$ be an algebraic extension of $F$, and let $f$ a monic irreducible polynomial in $F[X]$. If $f$ has a root in $E$, then $E/F$ is normal and separable iff every irreducible polynomial in $F[X]$ having a root in $E$ has $\deg f$ distinct roots in $E$. 
\end{proposition}

\begin{definition}
    (Galois Group)\par
    An extension $E/F$ of fields is \textbf{Galois} if it is finite, normal and separable. Then Aut$(E/F)$ is called  the \textbf{Galois group} of $E$ over $F$, and denoted by Gal$(E/F)$.
\end{definition}

\begin{theorem}
    For an extension $E/F$, the following statements are equivalent
    \begin{itemize}
        \item $E$ is the splitting field of a separable polynomial $f\in F[X]$
        \item $E$ is finite over $F$ and $F = E^{\text{Aut}(E/F)}$
        \item $F = E^G$ for some finite group $G$ of automorphisms of $E$
        \item $E$ is Galois over $F$
    \end{itemize}
\end{theorem}
\Pf\par
    (a) to (b), we know $E$ is finite over $F$ since it is generated by finite algebraic elements. Let $F' = E^{\text{Aut}(E/F)} \supset F$ and it suffices to show $F' = F$. Notice $f$ can be viewed as a polynomial in $F'[X]$ and hence
    \[|\text{Aut}(E/F')| = [E:F'] \leq [E:F] = |\text{Aut}(E/F)|\]
    and notice the equality of terms on both sides and hence $[E:F] = [E:F]$, which means $F' = F$. (b) to (c) trivial.\par
    (c) to (d), we know $E/F$ is finite by Artin's theorem. Let $\alpha \in E$ and $f$ the minimal polynomial of $\alpha$, and consider $\alpha_i$ the orbit of $\alpha$ under $G$ on $E$ with $\alpha_1 = 1$ and let $g(X) = \prod (X-\alpha_i)$ and it is easy to check $G\in F[X]$ and hence $f|g$. Conversely we will know that $g|f$ by use $\sigma\in G$ on $f$ and we know $f(\alpha_i) = 0 $ and hence $f=g$ and we are done.\par
    (d) to (a), assume $E = F[\alpha_1,\cdots,\alpha_m], \alpha_i \in E$ and let $f_i$ the minimal polynomial of $\alpha_i$ and $f$ the product of distinct $f_i$. $E$ normal implies that $f_i$ splits in $E$ and hence $E$ is the splitting field of $f$. $E$ separable means that $f_i$ separable and hence $f$ separable since $f_i$ will be coprime. 

\begin{corollary}
    Let $G$ be a finite groups of automorphisms of a field $E$, and let $F = E^G$. Then $E$ is a Galois extension of $F$ with Galois group $G$, and $[E:F] = |G|$.
\end{corollary}
\Pf\par
    $E$ is Galois by the theorem, and $G$ is the Galois group by corollary 2.3.3., and $[E:F] = |\text{Aut}(E/F)| = |G|$.

\begin{corollary}
    Every finite separable extension $E$ of $F$ is contained in a Galois extension.
\end{corollary}
\Pf\par
    Let $E = F[\alpha_1,\cdots,\alpha_m]$ and $f_i$ the minimal polynomial of $\alpha_i$, the the product of the distinct $f_i$ is a separable polynomial in $F[X]$ whose splitting field is a Galois extension of $F$ containing $E$.

\begin{corollary}
    Let $E\supset M\supset F$, if $E$ is Galois over $F$, then it is Galois over $M$.
\end{corollary}
\Pf\par
    $E$ is the splitting field of some separable $f\in F[X]$ which is also a separable polynomial in $M[X]$.

\begin{definition}
    (Special Galois Groups)\par
    An extension $E$ of $F$ is \textbf{cyclic/abelian/solvable} if it is a Galois extension of $F$ with cyclic/abelian/solvable Galois group.
\end{definition}

\newpage

\subsubsection{Main Theorem}

\begin{definition}
    (Subextension)\par
    Let $E$ be an extension of $F$. A \textbf{subextension} of $E/F$ is an extension $M/F$ with $M\subset E$, i.e. a field $M$ with $F\subset M \subset E$.
\end{definition}

\begin{theorem}
    (Fundamental Theorem of Galois Theory)\par
    Let $E$ be a Galois extension of $F$ with Galois group $G$. The map $H\mapsto E^H$ is a bijection from the set of subgroups of $G$ to the set of subextensions of $E/F$,
    \[
    \{\text{subgroups }H\text{ of }G\}\leftrightarrow\{\text{subextensions }F\subset M \subset E\}
    \]
    with inverse $M\mapsto \text{Gal}(E/M)$. Moreover, we have
    \begin{itemize}
        \item $H_1 \supset H_2 \Leftrightarrow E^{H_1} \subset E^{H_2}$
        \item $(H_1:H_2) = [E^{H_2}:E^{H_1}]$
        \item $\sigma H \sigma^{-1} \leftrightarrow \sigma M$, i.e.
        \[ E^{\sigma H \sigma^{-1}} = \sigma(E^H),\quad \text{Gal}(E/\sigma M) = \sigma \text{Gal}(E/M)\sigma^{-1} \]
        \item $H$ is normal in $G \Leftrightarrow E^H$ is normal over $F$, in which case $\text{Gal}(E^H/F) \cong G/H$.
    \end{itemize} 
\end{theorem}
\Pf\par
    Let $H$ a subgroup of $G$, then we know $\text{Gal}(E/E^H) = H$ and if $M/F$ a subextension, then $E$ is Galois over $M$ and $E^{\text{Gal(E/M)}} = M$ and hence they are inverse maps.\par
    (a) $H_1 \supset H_2$ implies $E^{H_1} \subset E^{H_2}$ implies $\text{Gal}(E/E^{H_1}) \supset \text{Gal}(E/E^{H_2})$ and hence $H_1 \supset H_2$.\par
    (b) For $H$ subgroup, we know $|\text{Gal}(E/E^H)| = [E:E^H]$ and hence the conclusion is true for $H_2 = 1$. For general we know $(H_1:1) = (H_1:H_2)(H_2:1)$ and $[E:E^{H_1}] = [E:E^{H_2}][E^{H_2}:E^{H_1}]$ and we are done.\par
    (c)For $\tau \in G, \alpha \in E$, $\tau \alpha = \alpha \Leftrightarrow \sigma\tau^{-1}\sigma\alpha = \sigma\alpha$ and hence $\tau$ fixes $M$ iff $\sigma\tau\sigma^{-1}$ fixed $\sigma M$ and so $\text{Gal}(E/\sigma M) = \sigma\text{Gal}(E/M)\sigma^{-1}$ and hence $E^{\sigma H \sigma^{-1}} = \sigma E^{H}$ and use the theorem 3.8.\par
    (d) Assume $H$ normal, then we know $\sigma E^H = E^H$ for all $\sigma\in G$ and hence consider $\sigma\mapsto \sigma|_{E^H}: G \to \text{Aut}(E^H/F)$ whose kernel is $H$ and notice $(E^H)^{\text{Aut}(E^H/F)} = F$ and hence $E^H$ is Galois oevr $F$ since $\text{Aut}(E^H/F) \cong G/H$ and we are done.\par
    Suppose $M$ normal and $\alpha_1.\cdots,\alpha_m$ generate $M$ over $F$. For $\sigma \in G$, $\sigma\alpha_i$ is a root of the minimal polynomial of $\alpha_i$ over $F$ and hence in $M$, which means $\sigma M = M$ and this implies that $\sigma H \sigma^{-1} = H$ and we are done.

\begin{proposition}
    Let $E$ and $L$ be extensions of $F$ contained in some common field. If $E/F$ is Galois, then $EL/L$ and $E/E\cap L$ are Galois and the map
    \[
    \sigma\mapsto \sigma|_E:\text{Gal}(EL/L) \to \text{Gal}(E/E\cap L)
    \]
    is an isomorphism.
\end{proposition}
\Pf\par
    If $E$ is Galois over $F$, it is the splitting field of a separable polynomial $f\in F[X] \subset L[X]$ and hence $EL$ is the splitting field of $f$ and $E$ is Galois over $E\cap L$ by $F\subset E\cap L$. Every automorphism $\sigma$ of $EL$ fixing the elements of $L$ maps roots of $f$ to roots of $f$ and hence $\sigma E = E$ and hence $\sigma\mapsto \sigma E: \text{Gal}(EL/L) \to \text{Gal}(E/E\cap L)$.\par
    If $\sigma \in \text{Gal}(EL/L)$ fiexes the elements of $E$, then it fixes the elements of $EL$ and hence $\sigma \mapsto \sigma|_E$ is injective. If $\alpha\in E$ is fixed by all $\sigma \in \text{Gal}(EL/L)$, then $\alpha \in E\cap L$ and hence $\sigma\mapsto \sigma|_E$ is surjective.

\begin{corollary}
    Suppose that $L$ is finite over $F$. Then
    \[
    [EL:F] = \dfrac{[E:F][L:F]}{[E\cap L :F]}
    \]
\end{corollary}
\Pf\par
    We have
    \[
    [EL:F] = [EL:L][L:F] = [E:E\cap  L][L:F] = \dfrac{[E:F][L:F]}{[E\cap L :F]}
    \]

\begin{proposition}
    Let $E_1$ and $E_2$ be extensions of $F$ contained in some common field. If $E_1$ and $E_2$ are Galois over $F$, then $E_1E_2$ and $E_1\cap E_2$ are Galois over $F$ and the map
    \[
    \sigma\mapsto (\sigma|_{E_1},\sigma|_{E_2}): \text{Gal}(E_1E_2/F) \to \text{Gal}(E_1/F)\times \text{Gal}(E_2/F)
    \]
    is an isomorphism of $\text{Gal}(E_1E_2/F)$ onto the subgroup $H = \{(\sigma_1,\sigma_2)| \sigma|_{E_1\cap E_2} = \sigma_2|_{E_1\cap E_2}\}$
    of $\text{Gal}(E_1/F) \times \text{Gal}(E_2/F)$
\end{proposition}
\Pf\par
    Let $a\in E_1\cap E_2$ and $f$ its minimal polynomial over $F$. Then $f$ has $\deg f$ distinct roots in $E_1$ and also in $E_2$, since it can have at most $f$ roots in $E_1E_2$ and the roots have to be in $E_1\cap E_2$, which means $E_1\cap E_2$ is normal separable and hence Galois. Also $E_1E_2$ is a splitting fields for some polynomial in $F[X]$ by $E_1,E_2$. The map $\sigma \mapsto (\sigma|_{E_1},\sigma)$ is obviously injective, and its image is in $H$.\par
    We know
    \[
    \text{Gal}(E_2/F)/\text{Gal}(E_2/E_1\cap E_2) \cong \text{Gal}(E_1\cap E_2/F)
    \]
    and so, for $\sigma_1\in \text{Gal}(E_1/F)$, $\sigma_1|_{E_1\cap E_2}$ has exactly $[E_2:E_1\cap E_2]$ to an element of $\text{Gal}(E_2/F)$ and hence
    \[
    |H| = [E_1:F][E_2:E_1\cap E_2] = \dfrac{[E_1:F][E_2:F]}{[E_1\cap E_2:F]} = [E_1E_2:F]
    \]

\begin{definition}
    (Galois Group of a Polynomial)\par
    If a polynomial $f\in F[X]$ is separable, then its splitting field $F_f$ is Galois over $F$ and we call $\text{Gal}(F_f/F)$ the Galois group $G_f$ of $f$. 
\end{definition}

\begin{proposition}
    For a separable polynomial $f\in F[X]$, we have $[F_f]|(\deg f)!$.
\end{proposition}
\Pf\par
    We know $G_f$ is consisted by the permutations $\sigma$ of the roots of $f$ such that for $P\in F[X_1,\cdots,X_{\deg f}]$, $P(\alpha_1,\cdots,\alpha_{\deg f}) = 0$ implies that $P(\sigma\alpha_1,\cdots,\sigma\alpha_{\deg f}) = 0$ because of the dimension and we are done.

% ------------------------------------------------------------------------------
% Reference and Cited Works
% ------------------------------------------------------------------------------
\newpage

\bibliographystyle{IEEEtran}
\bibliography{References.bib}

% ------------------------------------------------------------------------------

\end{document}
